### 2019-11-08 simple_ml/example/report1/paper.tex
add report.

\documentclass[journal, a4paper]{IEEEtran}

% some very useful LaTeX packages include:

%\usepackage{cite}      % Written by Donald Arseneau
                        % V1.6 and later of IEEEtran pre-defines the format
                        % of the cite.sty package \cite{} output to follow
                        % that of IEEE. Loading the cite package will
                        % result in citation numbers being automatically
                        % sorted and properly "ranged". i.e.,
                        % [1], [9], [2], [7], [5], [6]
                        % (without using cite.sty)
                        % will become:
                        % [1], [2], [5]--[7], [9] (using cite.sty)
                        % cite.sty's \cite will automatically add leading
                        % space, if needed. Use cite.sty's noadjust option
                        % (cite.sty V3.8 and later) if you want to turn this
                        % off. cite.sty is already installed on most LaTeX
                        % systems. The latest version can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/cite/

\usepackage{graphicx}   % Written by David Carlisle and Sebastian Rahtz
                        % Required if you want graphics, photos, etc.
                        % graphicx.sty is already installed on most LaTeX
                        % systems. The latest version and documentation can
                        % be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/required/graphics/
                        % Another good source of documentation is "Using
                        % Imported Graphics in LaTeX2e" by Keith Reckdahl
                        % which can be found as esplatex.ps and epslatex.pdf
                        % at: http://www.ctan.org/tex-archive/info/

%\usepackage{psfrag}    % Written by Craig Barratt, Michael C. Grant,
                        % and David Carlisle
                        % This package allows you to substitute LaTeX
                        % commands for text in imported EPS graphic files.
                        % In this way, LaTeX symbols can be placed into
                        % graphics that have been generated by other
                        % applications. You must use latex->dvips->ps2pdf
                        % workflow (not direct pdf output from pdflatex) if
                        % you wish to use this capability because it works
                        % via some PostScript tricks. Alternatively, the
                        % graphics could be processed as separate files via
                        % psfrag and dvips, then converted to PDF for
                        % inclusion in the main file which uses pdflatex.
                        % Docs are in "The PSfrag System" by Michael C. Grant
                        % and David Carlisle. There is also some information
                        % about using psfrag in "Using Imported Graphics in
                        % LaTeX2e" by Keith Reckdahl which documents the
                        % graphicx package (see above). The psfrag package
                        % and documentation can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/psfrag/

%\usepackage{subfigure} % Written by Steven Douglas Cochran
                        % This package makes it easy to put subfigures
                        % in your figures. i.e., "figure 1a and 1b"
                        % Docs are in "Using Imported Graphics in LaTeX2e"
                        % by Keith Reckdahl which also documents the graphicx
                        % package (see above). subfigure.sty is already
                        % installed on most LaTeX systems. The latest version
                        % and documentation can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/subfigure/

\usepackage{url}        % Written by Donald Arseneau
                        % Provides better support for handling and breaking
                        % URLs. url.sty is already installed on most LaTeX
                        % systems. The latest version can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/other/misc/
                        % Read the url.sty source comments for usage information.

%\usepackage{stfloats}  % Written by Sigitas Tolusis
                        % Gives LaTeX2e the ability to do double column
                        % floats at the bottom of the page as well as the top.
                        % (e.g., "\begin{figure*}[!b]" is not normally
                        % possible in LaTeX2e). This is an invasive package
                        % which rewrites many portions of the LaTeX2e output
                        % routines. It may not work with other packages that
                        % modify the LaTeX2e output routine and/or with other
                        % versions of LaTeX. The latest version and
                        % documentation can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/sttools/
                        % Documentation is contained in the stfloats.sty
                        % comments as well as in the presfull.pdf file.
                        % Do not use the stfloats baselinefloat ability as
                        % IEEE does not allow \baselineskip to stretch.
                        % Authors submitting work to the IEEE should note
                        % that IEEE rarely uses double column equations and
                        % that authors should try to avoid such use.
                        % Do not be tempted to use the cuted.sty or
                        % midfloat.sty package (by the same author) as IEEE
                        % does not format its papers in such ways.

\usepackage{amsmath}    % From the American Mathematical Society
                        % A popular package that provides many helpful commands
                        % for dealing with mathematics. Note that the AMSmath
                        % package sets \interdisplaylinepenalty to 10000 thus
                        % preventing page breaks from occurring within multiline
                        % equations. Use:
%\interdisplaylinepenalty=2500
                        % after loading amsmath to restore such page breaks
                        % as IEEEtran.cls normally does. amsmath.sty is already
                        % installed on most LaTeX systems. The latest version
                        % and documentation can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% Other popular packages for formatting tables and equations include:

%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty which improves the
% LaTeX2e array and tabular environments to provide better appearances and
% additional user controls. array.sty is already installed on most systems.
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

% V1.6 of IEEEtran contains the IEEEeqnarray family of commands that can
% be used to generate multiline equations as well as matrices, tables, etc.

% Also of notable interest:
% Scott Pakin's eqparbox package for creating (automatically sized) equal
% width boxes. Available:
% http://www.ctan.org/tex-archive/macros/latex/contrib/supported/eqparbox/

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.

% Your document starts here!
\begin{document}
\begin{titlepage}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for the horizontal lines, change thickness here

\center % Center everything on the page
 %----------------------------------------------------------------------------------------
%	LOGO SECTION
%----------------------------------------------------------------------------------------

~\\[1cm]
\includegraphics{SCUT.png}\\[2cm] % Include a department/university logo - this will require the graphicx package

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\HRule \\[1cm]
{ \huge \bfseries The Experiment Report of \textit{Machine Learning} }\\[0.6cm] % Title of your document
\HRule \\[2cm]
%----------------------------------------------------------------------------------------
%	HEADING SECTIONS
%----------------------------------------------------------------------------------------

\textsc{\LARGE \textbf{School:} School of Software Engineering}\\[1cm]
\textsc{\LARGE \textbf{Subject:} Software Engineering}\\[2cm]

%----------------------------------------------------------------------------------------
%	AUTHOR SECTION
%----------------------------------------------------------------------------------------

\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
Lizhao Liu % Your name
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
Mingkui Tan % Supervisor's Name
\end{flushright}
\end{minipage}\\[2cm]
~
\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Student ID:}\\
201730683109
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Grade:} \\
Undergraduate
\end{flushright}
\end{minipage}\\[2cm]

% If you don't want a supervisor, uncomment the two lines below and remove the section above
%\Large \emph{Author:}\\
%John \textsc{Smith}\\[3cm] % Your name

%----------------------------------------------------------------------------------------
%	DATE SECTION
%----------------------------------------------------------------------------------------

{\large \today}\\[2cm] % Date, change the \today to a set date if you want to be precise

%----------------------------------------------------------------------------------------

\vfill % Fill the rest of the page with whitespace

\end{titlepage}

% Define document title and author
	\title{Linear Regression, Ridge Regression \\and Gradient Descent}
	\maketitle

% Write abstract here
\begin{abstract}
In this report, we solve the Housing Dataset by using Linear Regression, Ridge Regression by closed form solution, and even optimize Linear Regression by Using Gradient Descen and its variants e.g. Stochastic Gradient Descent and Mini Batch Gradient Descent. \\
We perform experiments on four aspects: \\
1. Different lambdas in Ridge Regression \\
2. Comparision between Gradient Descent and its variants in terms of convergence and time-cost. \\
3. Tuning learning rate of Mini-Batch Gradient Descent. \\
4. Comparing the magnitude of $W$ between linear regression optimized by closed form solution, ridge regression and linear regression optimized by mini-batch Gradient Descent. \\
\end{abstract}

% Each section begins with a \section{title} command
\section{Introduction}
	% \PARstart{}{} creates a tall first letter for this first paragraph
\PARstart{T}{his} section introduces the problem to solved and leads the reader on to the main part. Detailed motivation is necessary. What's more, you can show your expected results and contributions.

% Main Part
\section{Methods and Theory}
In this section, you are asked to give a complete introduction to the experiment. For instance, the chosen methods, the related theories, the related equations(loss function), the derivation process(taking the gradient) and so on.

\section{Experiments}
\subsection{Dataset}
This section represents the related information of datasets, such as the content, the number of data, the training set, the validation set and so on.

\subsection{Implementation}
All detailed implementation in your experiment: initialization, process, results, all kinds of parameters. In a word, describe clearly What you do and how you do.\par

	% You can reference tables and figure by using the \ref{label} command. Each table and figure needs to have a UNIQUE label.
	Figures and tables should be labeled and numbered, such as in Table~\ref{tab:simParameters} and Fig.~\ref{fig:tf_plot}.

	% This is how you define a table: the [!hbt] means that LaTeX is forced (by the !) to place the table exactly here (by h), or if that doesnt work because of a pagebreak or so, it tries to place the table to the bottom of the page (by b) or the top (by t).
	\begin{table}[!hbt]
		% Center the table
		\begin{center}
		% Title of the table
		\caption{Simulation Parameters}
		\label{tab:simParameters}
		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
		\begin{tabular}{|c|c|}
			% To create a horizontal line, type \hline
			\hline
			% To end a column type &
			% For a linebreak type \\
			Information message length & $k=16000$ bit \\
			\hline
			Radio segment size & $b=160$ bit \\
			\hline
			Rate of component codes & $R_{cc}=1/3$\\
			\hline
			Polynomial of component encoders & $[1 , 33/37 , 25/37]_8$\\
			\hline
		\end{tabular}
		\end{center}
	\end{table}

	% If you have questions about how to write mathematical formulas in LaTeX, please read a LaTeX book or the 'Not So Short Introduction to LaTeX': tobi.oetiker.ch/lshort/lshort.pdf

	% This is how you include a eps figure in your document. LaTeX only accepts EPS or TIFF files.
	\begin{figure}[!hbt]
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{plot_tf}
		% Create a subtitle for the figure.
		\caption{Simulation results on the AWGN channel. Average throughput $k/n$ vs $E_s/N_0$.}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:tf_plot}
		\end{center}
	\end{figure}

\section{Conclusion}
	This section summarizes the paper. In our experiments, you can also write your gains and inspirations in here.

% Your document ends here!
\end{document}

### 2019-11-09 simple_ml/example/report1/paper.tex

@@
 
+\makeatletter
+\newif\if@restonecol
+\makeatother
+\let\algorithm\relax
+\let\endalgorithm\relax
+\usepackage[linesnumbered,ruled,vlined]{algorithm2e}%[ruled,vlined]{
+\usepackage{algpseudocode}
+\usepackage{amsmath}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}  % Use Input in the format of Algorithm
+\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm 
 % Other popular packages for formatting tables and equations include:
@@
 \begin{abstract}
-In this report, we solve the Housing Dataset by using Linear Regression, Ridge Regression by closed form solution, and even optimize Linear Regression by Using Gradient Descen and its variants e.g.
+In this report, we solve the house price prediction problem in Housing Dataset by using Linear Regression, Ridge Regression by closed form solution, and even Linear Regression optimized by using Gradient Descent and its variants e.g.
 Stochastic Gradient Descent and Mini Batch Gradient Descent.
@@
 We perform experiments on four aspects: \\
-1. Different lambdas in Ridge Regression \\
+1. Comparing the magnitude of $W$ between linear regression and ridge regression optimized by closed form solution. \\
 2. Comparision between Gradient Descent and its variants in terms of convergence and time-cost. \\
@@
 	% \PARstart{}{} creates a tall first letter for this first paragraph
-\PARstart{T}{his} section introduces the problem to solved and leads the reader on to the main part.
-Detailed motivation is necessary.
-What's more, you can show your expected results and contributions.
+\PARstart{L}{inear} Regression is the core of machine learning.
+Based on Linear Regression, many machine learning algorithm, such as Ridge Regression, Logistics Regression, SVM are developed.
+Even in many deep learning model, such as Covolutional Neural Network(CNN), Long Short Term Memory(LSTM), Gated Recurrent Unit(GRU), linear regression(or Linear Layer) is the basic component.
+So it is very important to fully exploit the insight of Linear Regression.
+To achieve that goal, In this experiment, we conduct many experiments on linear regression optimized by closed form solution and gradient descent, ridge regression by solving the house price predicting problem.
 
@@
 \section{Methods and Theory}
-In this section, you are asked to give a complete introduction to the experiment.
-For instance, the chosen methods, the related theories, the related equations(loss function), the derivation process(taking the gradient) and so on.
+In this part, we first define the Linear Regression, Mean Squared Error(MES) Loss function.
+Then we solve the closed form solution of Linear Regression and its variant Ridge Regression.
+At last we define gradient descent algorithm, and its variants schocastic gradient descent and mini batch gradient descent.
+\subsection{Linear Regression}
+Given dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, where $x_{i} \in \mathbf{R}^{n}$ and $y_{i} \in \mathbf{R}$.
+Liner Regression Model is parameterized by $(W, b)$, where $W \in \mathbf{R}^{n}$ and $b \in \mathbf{R}$ and the form of it is:
+ \begin{center}
+ 	\begin{equation}
+ 	y_{i} = x_{i}^{T}W + b
+ 	\end{equation}
+ \end{center} 
+We can write it in vertorized form:
+ \begin{center}
+	\begin{equation}
+	y = X^{T}W
+	\end{equation}
+\end{center} 
+where \\
+$\mathbf {y} ={\begin{pmatrix}y_{1}\\y_{2}\\\vdots \\y_{m}\end{pmatrix}},\quad 
+{\displaystyle X={\begin{pmatrix}1&\mathbf{x} _{1}^{\mathsf {T}}\\1&\mathbf {x} _{2}^{\mathsf {T}}\\\vdots&\vdots \\1&\mathbf {x} _{m}^{\mathsf {T}}\end{pmatrix}}={\begin{pmatrix}1&x_{11}&\cdots &x_{1n}\\1&x_{21}&\cdots &x_{2n}\\\vdots &\vdots &\ddots &\vdots \\1&x_{m1}&\cdots &x_{mn}\end{pmatrix}},} \\
+{\displaystyle {\boldsymbol {W }}={\begin{pmatrix}b \\W_{1}\\W_{2}\\\vdots \\W_{n}\end{pmatrix}}.}$
+\subsection{Mean Squared Error}
+Given the prediction of Linear Model $\hat{y} = X^{T}W $ and the Ground truth $y$, the MSE loss function is:
+ \begin{center}
+	\begin{equation}
+	L(\hat{y}, y) = \frac{1}{2m} \Sigma_{i=1}^{m}(\hat{y}_i, y_i) 
+				= \frac{1}{2m}(\hat{y} - y)^{T}(\hat{y} - y)
+	\end{equation}
+\end{center} 
+\subsection{Closed form Solution}
+The best parameter $W^{*}$ can be obtained by \\
+\begin{equation}
+ W^{*} = \arg\min_{W}L(X^{T}W, y)  
+\end{equation}
+So, we set 
+\begin{equation}
+\frac{\partial L(\hat{y}, y)}{\partial W} = 0 \\
+\end{equation}
+We can get 
+\begin{equation}
+W^{*} = (X^{T}X)^{-1}X^{T}y
+\end{equation}
+\subsection{Ridge Regression}
+In equation 6, when $m > n$, $X^{T}X$ is not invertible. Ridge Regression tackle this problem by adding a small term. So the closed form solution for Ridge Regression is
+\begin{equation}
+W_{ridge}^{*} = (X^{T}X + \lambda \mathbf{I})^{-1}X^{T}y
+\end{equation}
+In this way, the loss function for Ridge Regression is
+\begin{equation}
+L_{ridge}(\hat{y}, y) = \frac{1}{2m}(\hat{y} - y)^{T}(\hat{y} - y)  + \frac{1}{2} W^{T} W
+\end{equation}
+In another point of view, Ridge Regression can be seen as a regularized form of Linear Regression.
+\subsection{Gradient Descent}
+Not all problem can be derived a closed form solution, which is often the case in machine learning.
+So instead of getting the best parameters $W^{*}$ immedeatly, we can update it incremently until $W$ gets closed enough to $W^{*}$.
+That is the basic idea of Gradient Descent Algorithm.
+Gradient Descent Algorithm can be found in Algorithm~\ref{alg: Gradient_Descent}.
+\begin{algorithm}
+
+	\label{alg: Gradient_Descent}
+	\caption{Gradient Descent}
+	\KwIn{Training Dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, learning rate $\eta $, max iteration $ N$, parameter $W$}
+	\KwOut{Optimized parameter $\hat{W}$}
+	$t \gets 1$ \\
+	\For{$t < N $}
+	{
+		$\hat{y} \gets X^{T}W $ \\
+		$ L(\hat{y}, y) \gets \frac{1}{2m}(\hat{y} - y)^{T}(\hat{y} - y)$ \\
+		$\Delta{W} \gets \frac{\partial L}{\partial W}$ \\
+		$W \gets W - \eta * \Delta{W}$ \\
+	}
+	$\hat{W} = W$ \\
+	return $\hat{W}$
+\end{algorithm}
+
+\subsection{Stochastic Gradient Descent}
+Different from gradient descent which updates after it computes the gradient of parameter over all example, stochastic gradient descent updates immediately once it computes parameter's gradient from only one example.
+Stochastic Gradient Descent Algorithm can be found in Algorithm~\ref{alg: Stochastic_Gradient_Descent}.
+It can be seen in the algorithm that, there is another for loop inside the for loop of gradient descent algorithm.
+\begin{algorithm}
+		\label{alg: Stochastic_Gradient_Descent}
+	\caption{Stochastic Gradient Descent}
+	\KwIn{Training Dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, learning rate $\eta $, max iteration $ N$, parameter $W$}
+	\KwOut{Optimized parameter $\hat{W}$}
+	$t \gets 1$ \\
+	\For{$t < N $}
+	{
+		$ i \gets 0 $ \\
+		\For{$ i < m $}
+		{
+			$\hat{y}_{i} \gets X^{T}_{i}W $ \\
+			$ L(\hat{y}_{i}, y_{i}) \gets \frac{1}{2}(\hat{y}_{i} - y_{i})^{T}(\hat{y}_{i} - y_{i})$ \\
+			$\Delta{W} \gets \frac{\partial L}{\partial W}$ \\
+			$W \gets W - \eta * \Delta{W}$ \\
+		}
+	}
+	$\hat{W} = W$ \\
+	return $\hat{W}$
+\end{algorithm}
+
+\subsection{Mini Batch Gradient Descent}
+Due to the fact that stochastic gradient descent updates the parameter based on only one examples, which it is time-comsuming, mini batch gradient descent updates the parameter based on a batch of examples, typically the batch size is bigger than 1 and smaller than the number of whole examples, e.g.
+8, 16, 32...
+Mini Batch Gradient Descent Algorithm can be found in Algorithm~\ref{alg: Mini_Batch_Gradient_Descent}.
+\begin{algorithm}
+	\label{alg: Mini_Batch_Gradient_Descent}
+	\caption{Mini Batch Gradient Descent}
+	\KwIn{Training Dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, learning rate $\eta $, max iteration $ N$, parameter $W$}
+	\KwOut{Optimized parameter $\hat{W}$}
+	$t \gets 1$ \\
+	\For{$t < N $}
+	{
+		$ i \gets 0 $ \\
+		\For{$ X_{batch}, y_{batch} $ in $D$}
+		{
+			$\hat{y}_{batch} \gets X^{T}_{batch}W $ \\
+			$ L(\hat{y}_{batch}, y_{batch}) \gets \frac{1}{2}(\hat{y}_{batch} - y_{batch})^{T}(\hat{y}_{batch} - y_{batch})$ \\
+			$\Delta{W} \gets \frac{\partial L}{\partial W}$ \\
+			$W \gets W - \eta * \Delta{W}$ \\
+		}
+	}
+	$\hat{W} = W$ \\
+	return $\hat{W}$
+\end{algorithm}
 
@@
 \subsection{Dataset}
-This section represents the related information of datasets, such as the content, the number of data, the training set, the validation set and so on.
+We conduct all the experiments on housing dataset, which has total 506 examples and each example's form is $(x, y)$, where $x \in \mathbf{R}^{13}$ and $y \in \mathbf{R}$.
+We split the dataset into three part: 272 training examples, 67 validation examples and 167 test examples.
+$X$ is already scaled between $-1$ and $1$.
+And we normalized the $X_{train}, X_{validation}, X_{test} $ by using the mean and variance of $X_{train}$.
 
 \subsection{Implementation}
-All detailed implementation in your experiment: initialization, process, results, all kinds of parameters. In a word, describe clearly What you do and how you do.\par
+We implement the Linear Regression, Ridge Regression and Gradien Descent Algorithm using python and mainly rely on the numpy package.
 
-	% You can reference tables and figure by using the \ref{label} command. Each table and figure needs to have a UNIQUE label.
-	Figures and tables should be labeled and numbered, such as in Table~\ref{tab:simParameters} and Fig.~\ref{fig:tf_plot}.
-
-	% This is how you define a table: the [!hbt] means that LaTeX is forced (by the !) to place the table exactly here (by h), or if that doesnt work because of a pagebreak or so, it tries to place the table to the bottom of the page (by b) or the top (by t).
+\subsection{Linear Regression and Ridge Regression}
+In this section, we conduct the experiment of serveral magtitude of $\lambda$, which leads to serveral $W_{ridge}$.
+We use $L_2{norm}$ to represent the magtitude of a vector.
+And we evaluate the performance on housing data's test set.
+Given $v \in \mathbf{R}^{n}$
+\begin{equation}
+	L_2norm(v) = \sqrt{\Sigma_{i=1}^{n} v_{i}}
+\end{equation} \par
+From Table~\ref{tab:Ridge_Regression}, we can see that: \par
+First, as the magtitude of lambda becomes bigger, both $MSE_{train}$ and $MSE_{val}$ become bigger. \par
+Second, as the magtitude of lambda becomes bigger, the magtitude of $W_{ridge}$ become smaller. \par
+The first observation is not often the cases. But the second observation can be explained that as the regularizer $\lambda$ become bigger, the $W$ is regularized, so that it is smaller. \par
+By comparing Table~\ref{tab:Ridge_Regression} and Table~\ref{tab:Linear_Regression}, we can see that, the performance and the weight magtitude is almost the same as the $\lambda$ is small, but the difference become larger as $\lambda$ grows.
 \begin{table}[!hbt]
@@
 		% Title of the table
-		\caption{Simulation Parameters}
-		\label{tab:simParameters}
+		\caption{Different lambdas' impact in terms of error and $W$ magtitude.}
+		\label{tab:Ridge_Regression}
 		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
-		\begin{tabular}{|c|c|}
+		\begin{tabular}{|c|c|c|c|c|c|c|c|}
 			% To create a horizontal line, type \hline
@@
 			% For a linebreak type \\
-			Information message length & $k=16000$ bit \\
+			$log_{10}^{\lambda}$ & -2 & -1 & 0 & 1 & 2 & 3 \\
 			\hline
-			Radio segment size & $b=160$ bit \\
+			$MSE_{train}$   & 10.23 & 10.23 & 10.24 & 10.63 & 30.37 & 181.35   \\
 			\hline
-			Rate of component codes & $R_{cc}=1/3$\\
+			$MSE_{val}$  & 17.08 & 17.09 & 17.16 & 18.20 & 43.92 & 214.55   \\
 			\hline
-			Polynomial of component encoders & $[1 , 33/37 , 25/37]_8$\\
+			$L_2norm(W_{ridge})$  & 0.83 & 0.82 & 0.81 & 0.72 & 0.50 & 0.38 \\
 			\hline
@@
 
-	% If you have questions about how to write mathematical formulas in LaTeX, please read a LaTeX book or the 'Not So Short Introduction to LaTeX': tobi.oetiker.ch/lshort/lshort.pdf
+\begin{table}[!hbt]
+	% Center the table
+	\begin{center}
+		% Title of the table
+		\caption{Linear Regression Error and $W$ magtitude.}
+		\label{tab:Linear_Regression}
+		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
+		\begin{tabular}{|c|c|}
+			% To create a horizontal line, type \hline
+			\hline
+			$MSE_{train}$ & 10.23    \\
+			\hline
+			$MSE_{val}$ & 17.08    \\
+			\hline
+			$L_2norm(W)$ & 0.83  \\
+			\hline
+		\end{tabular}
+	\end{center}
+\end{table}
 
-	% This is how you include a eps figure in your document. LaTeX only accepts EPS or TIFF files.
-	\begin{figure}[!hbt]
-		% Center the figure.
-		\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{plot_tf}
-		% Create a subtitle for the figure.
-		\caption{Simulation results on the AWGN channel. Average throughput $k/n$ vs $E_s/N_0$.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:tf_plot}
-		\end{center}
-	\end{figure}
+\subsection{Gradient Descent, Stochastic Gradient Descent and Mini Batch Gradient Descent}
+In this section, we conduct experiments on optimizing the linear regression model by using three gradient descent algorrithms, and compare them in terms of convergence and time cost.
 
@@
 % Your document ends here!
+
 \end{document}

### 2019-11-10 simple_ml/example/report1/paper.tex
add report1.

@@
 \begin{abstract}
-In this report, we solve the house price prediction problem in Housing Dataset by using Linear Regression, Ridge Regression by closed form solution, and even Linear Regression optimized by using Gradient Descent and its variants e.g.
-Stochastic Gradient Descent and Mini Batch Gradient Descent.
+In this report, we solve the house price prediction problem in Housing Dataset by using closed form solution(CFS) optimized linear regression(LR), CSF optimized ridge regression(RR), and LR optimized by Gradient Descent(GD) and its variants e.g.
+Stochastic Gradient Descent(SGD) and Mini Batch Gradient Descent(MBGD).
 \\
 We perform experiments on four aspects: \\
-1. Comparing the magnitude of $W$ between linear regression and ridge regression optimized by closed form solution. \\
-2. Comparision between Gradient Descent and its variants in terms of convergence and time-cost. \\
-3. Tuning learning rate of Mini-Batch Gradient Descent. \\
-4. Comparing the magnitude of $W$ between linear regression optimized by closed form solution, ridge regression and linear regression optimized by mini-batch Gradient Descent. \\
+1. Comparision between CFS optimized LR and CFS optimized RR. \\
+2. Comparision between GD, SGD, MBGD in terms of convergence and time-cost. \\
+3. Tuning learning rate in MBGD. \\
+4. Comparision between CFS optimized and MBGD optimized LR. \\
 \end{abstract}
@@
 \PARstart{L}{inear} Regression is the core of machine learning.
-Based on Linear Regression, many machine learning algorithm, such as Ridge Regression, Logistics Regression, SVM are developed.
-Even in many deep learning model, such as Covolutional Neural Network(CNN), Long Short Term Memory(LSTM), Gated Recurrent Unit(GRU), linear regression(or Linear Layer) is the basic component.
-So it is very important to fully exploit the insight of Linear Regression.
-To achieve that goal, In this experiment, we conduct many experiments on linear regression optimized by closed form solution and gradient descent, ridge regression by solving the house price predicting problem.
+Based on it, many machine learning algorithm, such as RR, Logistics Regression, SVM are developed.
+Even in many deep learning model, such as Covolutional Neural Network(CNN), Long Short Term Memory(LSTM), Gated Recurrent Unit(GRU), LR(or Linear Layer) is the basic component.
+So it is very important to fully exploit the insight of LR.
+To achieve that goal, In this experiment, we conduct many experiments on CSF optimized LR, CSF optimized RR, MBGD optimized LR by solving the house price predicting problem.
 
@@
 $\mathbf {y} ={\begin{pmatrix}y_{1}\\y_{2}\\\vdots \\y_{m}\end{pmatrix}},\quad 
-{\displaystyle X={\begin{pmatrix}1&\mathbf{x} _{1}^{\mathsf {T}}\\1&\mathbf {x} _{2}^{\mathsf {T}}\\\vdots&\vdots \\1&\mathbf {x} _{m}^{\mathsf {T}}\end{pmatrix}}={\begin{pmatrix}1&x_{11}&\cdots &x_{1n}\\1&x_{21}&\cdots &x_{2n}\\\vdots &\vdots &\ddots &\vdots \\1&x_{m1}&\cdots &x_{mn}\end{pmatrix}},} \\
-{\displaystyle {\boldsymbol {W }}={\begin{pmatrix}b \\W_{1}\\W_{2}\\\vdots \\W_{n}\end{pmatrix}}.}$
+{\displaystyle {\boldsymbol {W }}={\begin{pmatrix}b \\W_{1}\\W_{2}\\\vdots \\W_{n}\end{pmatrix}},} \\
+{\displaystyle X={\begin{pmatrix}1&\mathbf{x} _{1}^{\mathsf {T}}\\1&\mathbf {x} _{2}^{\mathsf {T}}\\\vdots&\vdots \\1&\mathbf {x} _{m}^{\mathsf {T}}\end{pmatrix}}={\begin{pmatrix}1&x_{11}&\cdots &x_{1n}\\1&x_{21}&\cdots &x_{2n}\\\vdots &\vdots &\ddots &\vdots \\1&x_{m1}&\cdots &x_{mn}\end{pmatrix}}.} \\
+$
 \subsection{Mean Squared Error}
@@
  W^{*} = \arg\min_{W}L(X^{T}W, y)  
-\end{equation}
+\end{equation} \par
 So, we set 
@@
 \frac{\partial L(\hat{y}, y)}{\partial W} = 0 \\
-\end{equation}
+\end{equation} \par
 We can get 
 \begin{equation}
+\label{eq:cfs}
 W^{*} = (X^{T}X)^{-1}X^{T}y
@@
 \subsection{Ridge Regression}
-In equation 6, when $m > n$, $X^{T}X$ is not invertible. Ridge Regression tackle this problem by adding a small term. So the closed form solution for Ridge Regression is
+In Equation~\ref{eq:cfs}, when $m > n$, $X^{T}X$ is not invertible. Ridge Regression tackle this problem by adding a small term. So the closed form solution for Ridge Regression is
 \begin{equation}
 W_{ridge}^{*} = (X^{T}X + \lambda \mathbf{I})^{-1}X^{T}y
-\end{equation}
+\end{equation} \par
+Where $\mathbf{I}$ is identity matrix. \par
 In this way, the loss function for Ridge Regression is
@@
 	}
-	$\hat{W} = W$ \\
+	$\hat{W} \gets W$ \\
 	return $\hat{W}$
@@
 \subsection{Stochastic Gradient Descent}
-Different from gradient descent which updates after it computes the gradient of parameter over all example, stochastic gradient descent updates immediately once it computes parameter's gradient from only one example.
-Stochastic Gradient Descent Algorithm can be found in Algorithm~\ref{alg: Stochastic_Gradient_Descent}.
+Different from SD which updates after it computes the gradient of parameter over all examples, stochastic gradient descent updates immediately once it computes parameter's gradient from only one example.
+SGD Algorithm can be found in Algorithm~\ref{alg: Stochastic_Gradient_Descent}.
 It can be seen in the algorithm that, there is another for loop inside the for loop of gradient descent algorithm.
@@
 \subsection{Mini Batch Gradient Descent}
-Due to the fact that stochastic gradient descent updates the parameter based on only one examples, which it is time-comsuming, mini batch gradient descent updates the parameter based on a batch of examples, typically the batch size is bigger than 1 and smaller than the number of whole examples, e.g.
+Due to the fact that SGD updates the parameter based on only one examples, which it is time-comsuming, mini batch gradient descent updates the parameter based on a batch of examples, typically the batch size is bigger than 1 and smaller than the number of whole examples, e.g.
 8, 16, 32...
-Mini Batch Gradient Descent Algorithm can be found in Algorithm~\ref{alg: Mini_Batch_Gradient_Descent}.
+MBGD Algorithm can be found in Algorithm~\ref{alg: Mini_Batch_Gradient_Descent}.
 \begin{algorithm}
@@
 \subsection{Linear Regression and Ridge Regression}
-In this section, we conduct the experiment of serveral magtitude of $\lambda$, which leads to serveral $W_{ridge}$.
-We use $L_2{norm}$ to represent the magtitude of a vector.
-And we evaluate the performance on housing data's test set.
+In this section, we conduct the experiment of serveral magnitude of $\lambda$, which leads to serveral $W_{ridge}$.
+We use $L_2{norm}$ to represent the magnitude of a vector.
 Given $v \in \mathbf{R}^{n}$
@@
 From Table~\ref{tab:Ridge_Regression}, we can see that: \par
-First, as the magtitude of lambda becomes bigger, both $MSE_{train}$ and $MSE_{val}$ become bigger. \par
-Second, as the magtitude of lambda becomes bigger, the magtitude of $W_{ridge}$ become smaller. \par
+First, as the magnitude of lambda becomes bigger, both $MSE_{train}$ and $MSE_{val}$ become bigger. \par
+Second, as the magnitude of lambda becomes bigger, the magnitude of $W_{ridge}$ become smaller. \par
 The first observation is not often the cases. But the second observation can be explained that as the regularizer $\lambda$ become bigger, the $W$ is regularized, so that it is smaller. \par
-By comparing Table~\ref{tab:Ridge_Regression} and Table~\ref{tab:Linear_Regression}, we can see that, the performance and the weight magtitude is almost the same as the $\lambda$ is small, but the difference become larger as $\lambda$ grows.
+By comparing Table~\ref{tab:Ridge_Regression} and Table~\ref{tab:Linear_Regression}, we can see that, the performance and the weight magnitude is almost the same as the $\lambda$ is small, but the difference become larger as $\lambda$ grows.
+\par
+We also explore the weight mantitude between linear regression and ridge regression under different $\lambda$ magnitude setting.
+Specifically, we set $log_{10}^{\lambda}$ in range from -7 to 3.
+We can see from Fig~\ref{fig:ridge_w}, as the magnitude of $\lambda$ growing, the weight magnitude of ridge regression become much smaller than linear regression.
+\par
 \begin{table}[!hbt]
@@
 		% Title of the table
-		\caption{Different lambdas' impact in terms of error and $W$ magtitude.}
+		\caption{Different lambdas' impact in terms of error and $W$ magnitude.}
 		\label{tab:Ridge_Regression}
@@
 		% Title of the table
-		\caption{Linear Regression Error and $W$ magtitude.}
+		\caption{Linear Regression Error and $W$ magnitude.}
 		\label{tab:Linear_Regression}
@@
 
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{ridge_w}
+		% Create a subtitle for the figure.
+		\caption{The magnitude of $W_{ridge}$ under different lambda mgnitude.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:ridge_w}
+	\end{center}
+\end{figure}
+
 \subsection{Gradient Descent, Stochastic Gradient Descent and Mini Batch Gradient Descent}
-In this section, we conduct experiments on optimizing the linear regression model by using three gradient descent algorrithms, and compare them in terms of convergence and time cost.
+In this section, we conduct experiments on optimizing the linear regression model by using three gradient descent algorrithms, and compare them in terms of convergence and time cost. \par
+We first evaluate the convergence of three algorithm, specificlly we set batch size in a range from 1 to number of full examples in training set.
+When the batch size is one, mini batch gradient descent becomes stochastic gradient descent and when the batch size equals to number of full examples, mini batch gradient descent becomes gradient descent.
+All experiments are with the same learning rate 0.01.\par
+As we can see from Fig~\ref{fig:batch_size_train} and Fig~\ref{fig:batch_size_val}, as the batch size become larger, the convergence of the linear regression model bocome slower.
+The reason is that, in each epoch, the smaller the batch size, the model have more update steps, so the convergence is faster.
+Especially, the stochastic gradient descent converges within 10 steps, while gradient descent requires nearly 400 steps, there is a 400x margin.\par
+We then mesure the time cost for each batch size. \par 
+As illustrated in Fig~\ref{fig:time_cost}, the smaller the batch size, more time cost is required, because of the explicit for loop in the Stochastic gradient descent and mini batch gradient descent.
+Especially, the gradient descent requires nearly 1 seconds in one step, while stochastic gradient descent require 60 seconds, there exist a 60x margin.
+% This is how you include a eps figure in your document. LaTeX only accepts EPS or TIFF files.
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{batch_size_train}
+		% Create a subtitle for the figure.
+		\caption{The $MSE$ of training set under different batch size.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:batch_size_train}
+	\end{center}
+\end{figure}
+
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{batch_size_val}
+		% Create a subtitle for the figure.
+		\caption{The $MSE$ of validation set under different batch size.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:batch_size_val}
+	\end{center}
+\end{figure}
+
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{time_cost}
+		% Create a subtitle for the figure.
+		\caption{The time cost of 100 epoches under different batch size.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:time_cost}
+	\end{center}
+\end{figure}
+
+\subsection{Impact of learning rate}
+In this section, we evaluate the impact of learning rate in mini batch gradient descent, we set batch size to 64 and epochs to 200. We set learning rate in a range e.g. 1e-4, 1e-3, 1e-2, 1e-1, 1. \par
+As presented in Fig~\ref{fig:lr_train} and Fig~\ref{fig:lr_val}, small learning rate tend to make the convergence smoothly, but need to get more epoches to fully converge.
+However, big learning rate make the convergence very fast, but will not guarateee that the convergence will be near the optimal(or local optimal).
+And big learning rate make the $MSE$ shaking around after a specific epoch.
+\par
+
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{lr_train}
+		% Create a subtitle for the figure.
+		\caption{The $MSE$ in training set under different learning rate.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:lr_train}
+	\end{center}
+\end{figure}
+
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{lr_val}
+		% Create a subtitle for the figure.
+		\caption{The $MSE$ in validation set under different learning rate.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:lr_val}
+	\end{center}
+\end{figure}
+
+\subsection{Weight magnitude between CSF and MBGD}
+In this section, we explore the weight magnitude($L_2norm$) between CSF and MBGD optimized weight of linear regression. \par
+
+Then, we experiment on comparing the weight magnitude of linear regression by closed form solution(CFS) and mini batch gradient descent(MBGD).
+In MBGD, we set learning rate to 0.01 and batch size to 64.
+We can see that MBGD optimized weight's magnitude is stable after some epoches.
+But MBGD optimized weight's magnitude has a large margin(e.g.
+about 0.6) to CFS optimized weight.
+The reason is still unclear.
+
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{mbgd_w}
+		% Create a subtitle for the figure.
+		\caption{The magnitude of $W_{mbgd}$ under different epoches..}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:mbgd_w}
+	\end{center}
+\end{figure}
 
 \section{Conclusion}
-	This section summarizes the paper. In our experiments, you can also write your gains and inspirations in here.
+In this report, we explore the
 

### 2019-11-10 simple_ml/example/report1/paper.tex
complete experiment1.

@@
 \begin{abstract}
-In this report, we solve the house price prediction problem in Housing Dataset by using closed form solution(CFS) optimized linear regression(LR), CSF optimized ridge regression(RR), and LR optimized by Gradient Descent(GD) and its variants e.g.
-Stochastic Gradient Descent(SGD) and Mini Batch Gradient Descent(MBGD).
+In this report, we solve the house price prediction problem in Housing Dataset by using closed form solution (CFS) optimized linear regression (LR), CSF optimized ridge regression (RR), and LR optimized by Gradient Descent (GD) and its variants e.g.
+Stochastic Gradient Descent (SGD) and Mini Batch Gradient Descent (MBGD).
 \\
@@
 \PARstart{L}{inear} Regression is the core of machine learning.
-Based on it, many machine learning algorithm, such as RR, Logistics Regression, SVM are developed.
-Even in many deep learning model, such as Covolutional Neural Network(CNN), Long Short Term Memory(LSTM), Gated Recurrent Unit(GRU), LR(or Linear Layer) is the basic component.
+Based on it, many machine learning algorithms, such as RR, Logistics Regression, SVM are developed.
+Even in many deep learning models, such as Covolutional Neural Network (CNN), Long Short Term Memory (LSTM), Gated Recurrent Unit (GRU), LR (or Linear Layer) is the basic component.
 So it is very important to fully exploit the insight of LR.
@@
 \section{Methods and Theory}
-In this part, we first define the Linear Regression, Mean Squared Error(MES) Loss function.
-Then we solve the closed form solution of Linear Regression and its variant Ridge Regression.
-At last we define gradient descent algorithm, and its variants schocastic gradient descent and mini batch gradient descent.
+In this part, we first define the LR, Mean Squared Error (MES) loss function.
+Then we solve the closed form solution for LR and its variant RR.
+At last we define GD algorithm, and its variants SGD and MBGD.
 \subsection{Linear Regression}
@@
 \subsection{Ridge Regression}
-In Equation~\ref{eq:cfs}, when $m > n$, $X^{T}X$ is not invertible. Ridge Regression tackle this problem by adding a small term. So the closed form solution for Ridge Regression is
+In Equation~\ref{eq:cfs}, when $n > m$, $X^{T}X$ is not invertible. Ridge Regression tackle this problem by adding a small term. So the CFS for RR is
 \begin{equation}
@@
 L_{ridge}(\hat{y}, y) = \frac{1}{2m}(\hat{y} - y)^{T}(\hat{y} - y)  + \frac{1}{2} W^{T} W
-\end{equation}
-In another point of view, Ridge Regression can be seen as a regularized form of Linear Regression.
+\end{equation} \par
+In another point of view, RR can be seen as a regularized version of LR.
 \subsection{Gradient Descent}
-Not all problem can be derived a closed form solution, which is often the case in machine learning.
-So instead of getting the best parameters $W^{*}$ immedeatly, we can update it incremently until $W$ gets closed enough to $W^{*}$.
-That is the basic idea of Gradient Descent Algorithm.
-Gradient Descent Algorithm can be found in Algorithm~\ref{alg: Gradient_Descent}.
+Not all problem can be derived a CFS, which is often the case in machine learning.
+So instead of getting the best parameters $W^{*}$ immedeatly, we can update it incremently until $W$ gets close enough to $W^{*}$.
+That is the basic idea of GD algorithm.
+GD algorithm can be found in Algorithm~\ref{alg: Gradient_Descent}.
 \begin{algorithm}
@@
 \subsection{Stochastic Gradient Descent}
-Different from SD which updates after it computes the gradient of parameter over all examples, stochastic gradient descent updates immediately once it computes parameter's gradient from only one example.
-SGD Algorithm can be found in Algorithm~\ref{alg: Stochastic_Gradient_Descent}.
-It can be seen in the algorithm that, there is another for loop inside the for loop of gradient descent algorithm.
+Different from GD which updates after it computes the gradient of parameters over all examples, stochastic gradient descent updates immediately once it computes parameters' gradient from only one example.
+SGD algorithm can be found in Algorithm~\ref{alg: Stochastic_Gradient_Descent}.
+It can be seen in the algorithm that, there is another for loop inside the for loop of GD algorithm, which leads to time un-efficiency.
 \begin{algorithm}
@@
 \subsection{Mini Batch Gradient Descent}
-Due to the fact that SGD updates the parameter based on only one examples, which it is time-comsuming, mini batch gradient descent updates the parameter based on a batch of examples, typically the batch size is bigger than 1 and smaller than the number of whole examples, e.g.
+Due to the fact that SGD updates the parameters based on only one examples, which it is time-comsuming, mini batch gradient descent updates the parameter based on a batch of examples, typically the batch size is bigger than 1 and smaller than the number of whole examples, e.g.
 8, 16, 32...
@@
 $X$ is already scaled between $-1$ and $1$.
-And we normalized the $X_{train}, X_{validation}, X_{test} $ by using the mean and variance of $X_{train}$.
+And we normalized the $X_{train}, X_{val}, X_{test} $ by using the mean and variance of $X_{train}$.
 
 \subsection{Implementation}
-We implement the Linear Regression, Ridge Regression and Gradien Descent Algorithm using python and mainly rely on the numpy package.
+We implement the LR, RR and GD, GD, MBGD algorithm using python and mainly rely on the numpy package.
 
 \subsection{Linear Regression and Ridge Regression}
-In this section, we conduct the experiment of serveral magnitude of $\lambda$, which leads to serveral $W_{ridge}$.
+In this section, we conduct the experiment of serveral magnitude of $\lambda$ of RR in training set, which leads to serveral $W_{ridge}$.
 We use $L_2{norm}$ to represent the magnitude of a vector.
@@
 \par
-We also explore the weight mantitude between linear regression and ridge regression under different $\lambda$ magnitude setting.
+We also explore the weight mantitude between LR and RR under different $\lambda$ magnitude setting.
 Specifically, we set $log_{10}^{\lambda}$ in range from -7 to 3.
@@
 		% Title of the table
-		\caption{Different lambdas' impact in terms of error and $W$ magnitude.}
+		\caption{Different lambdas' impact in terms of error and $W$ magnitude. Best result are in bold.}
 		\label{tab:Ridge_Regression}
@@
 			\hline
-			$MSE_{train}$   & 10.23 & 10.23 & 10.24 & 10.63 & 30.37 & 181.35   \\
+			$MSE_{train}$   & \textbf{10.23} & \textbf{10.23} & 10.24 & 10.63 & 30.37 & 181.35   \\
 			\hline
-			$MSE_{val}$  & 17.08 & 17.09 & 17.16 & 18.20 & 43.92 & 214.55   \\
+			$MSE_{val}$  & \textbf{17.08} & 17.09 & 17.16 & 18.20 & 43.92 & 214.55   \\
 			\hline
@@
 \subsection{Gradient Descent, Stochastic Gradient Descent and Mini Batch Gradient Descent}
-In this section, we conduct experiments on optimizing the linear regression model by using three gradient descent algorrithms, and compare them in terms of convergence and time cost. \par
-We first evaluate the convergence of three algorithm, specificlly we set batch size in a range from 1 to number of full examples in training set.
+In this section, we conduct experiments on optimizing the LR model by using GD, SGD, MBGD  algorrithms, and compare them in terms of convergence and time cost. \par
+We first evaluate the convergence of three algorithms, specificlly we set batch size in a range from 1 to number of full examples in training set.
 When the batch size is one, mini batch gradient descent becomes stochastic gradient descent and when the batch size equals to number of full examples, mini batch gradient descent becomes gradient descent.
@@
 Especially, the stochastic gradient descent converges within 10 steps, while gradient descent requires nearly 400 steps, there is a 400x margin.\par
-We then mesure the time cost for each batch size. \par 
-As illustrated in Fig~\ref{fig:time_cost}, the smaller the batch size, more time cost is required, because of the explicit for loop in the Stochastic gradient descent and mini batch gradient descent.
-Especially, the gradient descent requires nearly 1 seconds in one step, while stochastic gradient descent require 60 seconds, there exist a 60x margin.
+We then measure the time cost for each batch size. \par 
+As illustrated in Fig~\ref{fig:time_cost}, the smaller the batch size, more time cost is required, because of the explicit for loop in the SGD and MBGD.
+Especially, the GD requires only about 1 seconds in one step, while SGD requires 60 seconds, there exist a 60x margin.
+\par
 % This is how you include a eps figure in your document. LaTeX only accepts EPS or TIFF files.
@@
 \subsection{Impact of learning rate}
-In this section, we evaluate the impact of learning rate in mini batch gradient descent, we set batch size to 64 and epochs to 200. We set learning rate in a range e.g. 1e-4, 1e-3, 1e-2, 1e-1, 1. \par
-As presented in Fig~\ref{fig:lr_train} and Fig~\ref{fig:lr_val}, small learning rate tend to make the convergence smoothly, but need to get more epoches to fully converge.
-However, big learning rate make the convergence very fast, but will not guarateee that the convergence will be near the optimal(or local optimal).
-And big learning rate make the $MSE$ shaking around after a specific epoch.
+In this section, we evaluate the impact of learning rate in MBGD, we set batch size to 64 and epochs to 200. We set learning rate in a range e.g. 1e-4, 1e-3, 1e-2, 1e-1, 1. \par
+As presented in Fig~\ref{fig:lr_train} and Fig~\ref{fig:lr_val}, small learning rate tends to make the convergence smoothly, but needs more epoches to fully converge.
+However, big learning rate make the convergence very fast, but will not guarateee that the convergence will be near the optimal(or local optimal) and makes the $MSE$ shaking around after a specific epoch.
 \par
@@
 
-Then, we experiment on comparing the weight magnitude of linear regression by closed form solution(CFS) and mini batch gradient descent(MBGD).
+Then, we experiments on comparing the weight magnitude of CFS and MBGD optimized LR.
 In MBGD, we set learning rate to 0.01 and batch size to 64.
-We can see that MBGD optimized weight's magnitude is stable after some epoches.
+We can see that MBGD optimized LR's weight magnitude is stable after some epoches.
 But MBGD optimized weight's magnitude has a large margin(e.g.
@@
 The reason is still unclear.
+\par
 
@@
 
+\subsection{Performance} 
+In this section, we report the performance on CFS optimized LR, RR and MBGD optimized LR in training set, validation set and test set.
+The $\lambda$ is set to 1e-7 after validation.
+And batch size is set to 64 in MBGD, learing rate set to 0.01 and epoch set to 200 by validation.
+\par
+From Table~\ref{tab:Performance}, we can see that alougth MBGD optimized LR's $MSE_{train}$ and $MSE_{val}$ are not the best, but its result in $MSE_{test}$ is outstanding.
+The reason remains unclear, maybe the same reason that the magnitude between CFS optimized LR and MBGD optimized LR has a large margin.
+\par
+\begin{table}[!hbt]
+	% Center the table
+	\begin{center}
+		% Title of the table
+		\caption{Final Performance of CFS optimized LR, RR and MBGD optimized LR, best result are in bold.}
+		\label{tab:Performance}
+		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
+		\begin{tabular}{|c|c|c|c|}
+			% To create a horizontal line, type \hline
+			\hline
+			% To end a column type &
+			% For a linebreak type \\
+			& LR & RR & MBGD \\
+			\hline
+			$MSE_{train}$   & \textbf{10.23} & \textbf{10.23} & 11.37   \\
+			\hline
+			$MSE_{val}$  & \textbf{17.08} & \textbf{17.08} & 19.04   \\
+			\hline
+			$MSE_{test}$  & 10.20 &  10.20 & \textbf{10.14}  \\
+			\hline
+		\end{tabular}
+	\end{center}
+\end{table}
+
 \section{Conclusion}
-In this report, we explore the
+In this report, we explore the CFS optimized LR, CFS optimized RR and MBGD optimized LR.
+We conduct the experiments on the CFS optimized LR and RR in terms of performance and weight magnitude.
+We also explore GD, SGD, MBGD in terms of convergence and time efficiency.
+Moreover, we tuning the hyper-parameter learning rate in MBGD.
+We also compare the weight magnitude between CFS optimized LR and MBGD optimized LR.
+Finally, we report the performance in CFS optimized LR, RR and MBGD LR.
+After a series of experiments, we now get more insight of LR, RR and GD and its variants SGD and MBGD.
+\par
 

### 2019-11-10 setup.py
complete exp1.

@@ -2,7 +2,7 @@ from setuptools import setup, find_packages
 
 setup(
     name='pip_setup',
-    version='0.1.0',
+    version='0.1.1',
     description='simple: simple machine learning framework.',
     classifiers=[
         'License :: OSI Approved :: MIT License',

### 2019-11-10 simple_ml/example/report2/paper.tex
start exp2.

--- 2019-11-10 simple_ml/example/report1/paper.tex
@@
 % Define document title and author
-	\title{Linear Regression, Ridge Regression \\and Gradient Descent}
+	\title{Logistic Regression and SVM}
 	\maketitle
@@
 \begin{abstract}
-In this report, we solve the house price prediction problem in Housing Dataset by using closed form solution (CFS) optimized linear regression (LR), CSF optimized ridge regression (RR), and LR optimized by Gradient Descent (GD) and its variants e.g.
-Stochastic Gradient Descent (SGD) and Mini Batch Gradient Descent (MBGD).
-\\
+In this report, we solve the binary classification problem in a9a Dataset by using Logistic Regression (LR) and Support Vector Machine (SVM). \\
 We perform experiments on four aspects: \\

### 2019-11-11 simple_ml/example/report2/paper.tex
start exp2.

@@
 \begin{abstract}
-In this report, we solve the binary classification problem in a9a Dataset by using Logistic Regression (LR) and Support Vector Machine (SVM). \\
-We perform experiments on four aspects: \\
-1. Comparision between CFS optimized LR and CFS optimized RR. \\
-2. Comparision between GD, SGD, MBGD in terms of convergence and time-cost. \\
-3. Tuning learning rate in MBGD. \\
-4. Comparision between CFS optimized and MBGD optimized LR. \\
+In this report, we solve the binary classification problem in a9a dataset by Logistic Regression (LR) and Support Vector Machine (SVM). \\
+We perform experiments on three aspects: \\
+1. Loss function comparision in SVM. \\
+2. Hyper-parameter tuning in SVM. \\
+3. Initilizer comparision in both LR and SVM. \\
+4. Optimizer comparision in both LR and SVM. \\
 \end{abstract}

### 2019-11-11 simple_ml/example/report2/paper.tex
add report2.

@@
 In this report, we solve the binary classification problem in a9a dataset by Logistic Regression (LR) and Support Vector Machine (SVM). \\
-We perform experiments on three aspects: \\
+We perform experiments on four aspects: \\
 1. Loss function comparision in SVM. \\
@@
 	% \PARstart{}{} creates a tall first letter for this first paragraph
-\PARstart{L}{inear} Regression is the core of machine learning.
-Based on it, many machine learning algorithms, such as RR, Logistics Regression, SVM are developed.
-Even in many deep learning models, such as Covolutional Neural Network (CNN), Long Short Term Memory (LSTM), Gated Recurrent Unit (GRU), LR (or Linear Layer) is the basic component.
-So it is very important to fully exploit the insight of LR.
-To achieve that goal, In this experiment, we conduct many experiments on CSF optimized LR, CSF optimized RR, MBGD optimized LR by solving the house price predicting problem.
+\PARstart{L}{ogistic} Regression(LR) is an extension of linear regression, which use $\sigma$ function as activation to map the output of linear regression into a interval (0, 1).
+So that LR can output the probability in binary classification.
+SVM is also an extension of linear regression.
+Based on the idea "large margin classification", SVM can perform very well in many classification task.
+Even now, LR and SVM are widely used in academic and industry community.
+These two algorithms are classic, so we fully explore them by solving a9a binary classification task.
+Beyond that, we will explore the initilizer and optimizer selection in both LR and SVM.
 
@@
 \section{Methods and Theory}
-In this part, we first define the LR, Mean Squared Error (MES) loss function.
+In this part, we first define logistic regression and SVM.
+Then we define LR's loss function Binary Cross Entrophy (BCE) and SVM's loss function Hinge Loss (HL).
+Mean Squared Error (MES) loss function.
 Then we solve the closed form solution for LR and its variant RR.
 At last we define GD algorithm, and its variants SGD and MBGD.
-\subsection{Linear Regression}
-Given dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, where $x_{i} \in \mathbf{R}^{n}$ and $y_{i} \in \mathbf{R}$.
-Liner Regression Model is parameterized by $(W, b)$, where $W \in \mathbf{R}^{n}$ and $b \in \mathbf{R}$ and the form of it is:
+\subsection{Logistic Regression}
+Given dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, where $x_{i} \in \mathbf{R}^{n}$ and $y_{i} \in {0, 1}$. Mathematically, for a single training datapoint $(x, y)$, LR assumes: \par
  \begin{center}
 	\begin{equation}
- 	y_{i} = x_{i}^{T}W + b
+	P(Y = 1|X = x) = \sigma(z) 
 	\end{equation}
- \end{center} 
-We can write it in vertorized form:
- \begin{center}
 	\begin{equation}
-	y = X^{T}W
+	P(Y = 0|X = x) = 1 - \sigma(z)
 	\end{equation}
-\end{center} 
-where \\
-$\mathbf {y} ={\begin{pmatrix}y_{1}\\y_{2}\\\vdots \\y_{m}\end{pmatrix}},\quad 
-{\displaystyle {\boldsymbol {W }}={\begin{pmatrix}b \\W_{1}\\W_{2}\\\vdots \\W_{n}\end{pmatrix}},} \\
-{\displaystyle X={\begin{pmatrix}1&\mathbf{x} _{1}^{\mathsf {T}}\\1&\mathbf {x} _{2}^{\mathsf {T}}\\\vdots&\vdots \\1&\mathbf {x} _{m}^{\mathsf {T}}\end{pmatrix}}={\begin{pmatrix}1&x_{11}&\cdots &x_{1n}\\1&x_{21}&\cdots &x_{2n}\\\vdots &\vdots &\ddots &\vdots \\1&x_{m1}&\cdots &x_{mn}\end{pmatrix}}.} \\
-$
-\subsection{Mean Squared Error}
-Given the prediction of Linear Model $\hat{y} = X^{T}W $ and the Ground truth $y$, the MSE loss function is:
- \begin{center}
 	\begin{equation}
-	L(\hat{y}, y) = \frac{1}{2m} \Sigma_{i=1}^{m}(\hat{y}_i, y_i) 
-				= \frac{1}{2m}(\hat{y} - y)^{T}(\hat{y} - y)
+	z = F(x; W)
 	\end{equation}
-\end{center} 
-\subsection{Closed form Solution}
-The best parameter $W^{*}$ can be obtained by \\
+\end{center} \par
+where $F(x; W)$ is linear regression parameterized by $W$ and $\sigma(.)$ is sigmoid function, where $\sigma(z) = \frac{1}{1 + e^{-z}} \in (0, 1)$.
+\subsection{Binary Cross Entrophy}
+Logistic regression assume each datapoint is independent, so the likelihood of all data is: \par
 \begin{equation}
- W^{*} = \arg\min_{W}L(X^{T}W, y)  
+	\begin{aligned}
+	L(W) &= \prod_{i=1}^m P(Y = y_i | X = x_i) \\ &= \prod_{i=1}^m \sigma(z)^{y_i} (1 - \sigma(z)^{1 - y_i} )
+	\end{aligned}
 \end{equation} \par
-So, we set 
+
+So our goal is to maximize the likelihood of data, in practice we maximize the log likelihood. \par
 \begin{equation}
-\frac{\partial L(\hat{y}, y)}{\partial W} = 0 \\
+\begin{aligned}
+LL(W) &= log\prod_{i=1}^m \sigma(z)^{y_i} (1 - \sigma(z)^{1 - y_i} ) \\ &= \Sigma_{i=1}^{m} y_i \sigma(z) + (1 - y_i)(1 - \sigma(z))
+\end{aligned}
 \end{equation} \par
-We can get 
-\begin{equation}
-\label{eq:cfs}
-W^{*} = (X^{T}X)^{-1}X^{T}y
-\end{equation}
+
 \subsection{Ridge Regression}

### 2019-11-11 simple_ml/example/report2/paper.tex
partial complete exp2.

@@
 
-%\usepackage{subfigure} % Written by Steven Douglas Cochran
+\usepackage{subfigure} % Written by Steven Douglas Cochran
                         % This package makes it easy to put subfigures
@@
 We perform experiments on four aspects: \\
-1. Loss function comparision in SVM. \\
-2. Hyper-parameter tuning in SVM. \\
+1. Hyper-parameter tuning in SVM. \\
+2. Loss function comparision in SVM. \\
 3. Initilizer comparision in both LR and SVM. \\
@@
 \section{Methods and Theory}
-In this part, we first define logistic regression and SVM.
-Then we define LR's loss function Binary Cross Entrophy (BCE) and SVM's loss function Hinge Loss (HL).
-Mean Squared Error (MES) loss function.
-Then we solve the closed form solution for LR and its variant RR.
-At last we define GD algorithm, and its variants SGD and MBGD.
+In this part, we first define logistic regression and LR's loss function Binary Cross Entrophy (BCE). Then we define SVM and SVM's loss function Hinge Loss (HL).
 \subsection{Logistic Regression}
-Given dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, where $x_{i} \in \mathbf{R}^{n}$ and $y_{i} \in {0, 1}$. Mathematically, for a single training datapoint $(x, y)$, LR assumes: \par
+Given dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, where $x_{i} \in \mathbf{R}^{n}$ and $y_{i} \in \{0, 1\}$. Mathematically, for a single training datapoint $(x, y)$, LR assumes: \par
  \begin{center}
@@
 \subsection{Binary Cross Entrophy}
-Logistic regression assume each datapoint is independent, so the likelihood of all data is: \par
+Logistic regression assumes that each datapoint is independent, so the likelihood of all data is: \par
 \begin{equation}
@@
 \begin{aligned}
-LL(W) &= log\prod_{i=1}^m \sigma(z)^{y_i} (1 - \sigma(z)^{1 - y_i} ) \\ &= \Sigma_{i=1}^{m} y_i \sigma(z) + (1 - y_i)(1 - \sigma(z))
+LL(W) &= log\prod_{i=1}^m \sigma(z)^{y_i} (1 - \sigma(z)^{1 - y_i} ) \\ &= \Sigma_{i=1}^{m} (y_i \sigma(z) + (1 - y_i)(1 - \sigma(z)))
+\end{aligned}
+\end{equation} \par
+When using mini batch gradient descent (MBGD) algorithm, we want to minimize something, so we minimize the negative log likelihood. \par
+
+\begin{equation}
+\label{eqa: NLL}
+NLL(W) = -\Sigma_{i=1}^{m} (y_i \sigma(z) + (1 - y_i)(1 - \sigma(z)))
+\end{equation} \par
+Equation~\ref{eqa: NLL} is also called binary cross entropy.
+
+\subsection{SVM and Hinge Loss}
+Given dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, where $x_{i} \in \mathbf{R}^{n}$ and $y_{i} \in \{-1, 1\}$. SVM is based on linear regression. When given a data point, it wants: \par
+
+\begin{equation}
+\label{eqa:svm_two}
+\left\{
+\begin{array}{lr}
+w^{T}x + b \geq 1,~&if~y = 1  \\
+w^{T}x + b \leq -1,~&if~y = -1 \\
+\end{array}
+\right.
+\end{equation} \par
+Equation~\ref{eqa:svm_two} can also be written to:
+\begin{equation}
+	y(w^{T}x + b) \geq 1
+\end{equation} \par
+Other than make the classification correct, SVM also wants to make the classification boundary as safe as possible.
+To achieve that, it wants to make the margin between the positive class and negative class as large as possible.
+\par
+The positive boundary of SVM is $w^Tx + b = 1$ and negative boundary of SVM is $w^Tx + b = -1$. So the margin between this two boundary is: \par
+\begin{equation}
+	\label{eqa:margin}
+	Margin = \frac{2}{||w||}
+\end{equation} \par
+In practice, instead of maximize Equation~\ref{eqa:margin}, we want to minimize: \par
+\begin{equation}
+	\frac{w^Tw}{2}
+\end{equation} \par
+So, the optimization problem for SVM is:
+\begin{equation}
+	\begin{aligned}
+	\label{eqa:svm_optimization}
+	min_{w, b}~&\frac{w^Tw}{2} \\
+	s.t.~&y_i(w^Tx_i + b) \geq 1, i=1, 2, ..., m
 	\end{aligned}	
@@
 
-\subsection{Ridge Regression}
-In Equation~\ref{eq:cfs}, when $n > m$, $X^{T}X$ is not invertible. Ridge Regression tackle this problem by adding a small term. So the CFS for RR is
+Moreover, data point may not be linearly separable.
+Even the data point is linear separable, the outliers in dataset will hurt the performance of SVM.
+So, SVM introduce slack variable $\xi_i $ for each data point, which represents how much data point $i$ is on the wrong side of margin boundary.
+\par
+1. if $\xi_i = 0$, it is ok. \par
+2. if $ 0 < \xi_i < 1 $, the data point is correctly classified, but with a smaller margin than $\frac{1}{||w||}$. \par
+3. if $\xi_i > 1$, the data point is incorrectly classified. \par
+Then the optimization problem becomes: 
 \begin{equation}
-W_{ridge}^{*} = (X^{T}X + \lambda \mathbf{I})^{-1}X^{T}y
+	\begin{aligned}
+	\label{eqa:svm_soft_optimization}
+	min_{w, b}~&\frac{w^Tw}{2} + \frac{C}{m}\Sigma_{i=1}^m \xi_i \\
+	s.t.~&y_i(w^Tx_i + b) \geq 1 - \xi_i, i=1, 2, ..., m
+	\end{aligned}	
 \end{equation} \par
-Where $\mathbf{I}$ is identity matrix. \par
-In this way, the loss function for Ridge Regression is
+As $ \xi_i \geq 1 - y_i(w^Tx_i + b), i=1, 2, ..., m$, so
 \begin{equation}
-L_{ridge}(\hat{y}, y) = \frac{1}{2m}(\hat{y} - y)^{T}(\hat{y} - y)  + \frac{1}{2} W^{T} W
+\label{eqa:xi}
+\xi_i = 
+\left\{
+\begin{array}{lr}
+	1 - y_i(w^{T}x_i + b),&if~1 - y_i(w^{T}x_i + b) \geq 0  \\
+	0,&if~1 - y_i(w^{T}x_i + b) < 0  \\
+\end{array}
+\right.
 \end{equation} \par
-In another point of view, RR can be seen as a regularized version of LR.
-\subsection{Gradient Descent}
-Not all problem can be derived a CFS, which is often the case in machine learning.
-So instead of getting the best parameters $W^{*}$ immedeatly, we can update it incremently until $W$ gets close enough to $W^{*}$.
-That is the basic idea of GD algorithm.
-GD algorithm can be found in Algorithm~\ref{alg: Gradient_Descent}.
-\begin{algorithm}
-
-	\label{alg: Gradient_Descent}
-	\caption{Gradient Descent}
-	\KwIn{Training Dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, learning rate $\eta $, max iteration $ N$, parameter $W$}
-	\KwOut{Optimized parameter $\hat{W}$}
-	$t \gets 1$ \\
-	\For{$t < N $}
-	{
-		$\hat{y} \gets X^{T}W $ \\
-		$ L(\hat{y}, y) \gets \frac{1}{2m}(\hat{y} - y)^{T}(\hat{y} - y)$ \\
-		$\Delta{W} \gets \frac{\partial L}{\partial W}$ \\
-		$W \gets W - \eta * \Delta{W}$ \\
-	}
-	$\hat{W} \gets W$ \\
-	return $\hat{W}$
-\end{algorithm}
-
-\subsection{Stochastic Gradient Descent}
-Different from GD which updates after it computes the gradient of parameters over all examples, stochastic gradient descent updates immediately once it computes parameters' gradient from only one example.
-SGD algorithm can be found in Algorithm~\ref{alg: Stochastic_Gradient_Descent}.
-It can be seen in the algorithm that, there is another for loop inside the for loop of GD algorithm, which leads to time un-efficiency.
-\begin{algorithm}
-		\label{alg: Stochastic_Gradient_Descent}
-	\caption{Stochastic Gradient Descent}
-	\KwIn{Training Dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, learning rate $\eta $, max iteration $ N$, parameter $W$}
-	\KwOut{Optimized parameter $\hat{W}$}
-	$t \gets 1$ \\
-	\For{$t < N $}
-	{
-		$ i \gets 0 $ \\
-		\For{$ i < m $}
-		{
-			$\hat{y}_{i} \gets X^{T}_{i}W $ \\
-			$ L(\hat{y}_{i}, y_{i}) \gets \frac{1}{2}(\hat{y}_{i} - y_{i})^{T}(\hat{y}_{i} - y_{i})$ \\
-			$\Delta{W} \gets \frac{\partial L}{\partial W}$ \\
-			$W \gets W - \eta * \Delta{W}$ \\
-		}
-	}
-	$\hat{W} \gets W$ \\
-	return $\hat{W}$
-\end{algorithm}
-
-\subsection{Mini Batch Gradient Descent}
-Due to the fact that SGD updates the parameters based on only one examples, which it is time-comsuming, mini batch gradient descent updates the parameter based on a batch of examples, typically the batch size is bigger than 1 and smaller than the number of whole examples, e.g.
-8, 16, 32...
-MBGD Algorithm can be found in Algorithm~\ref{alg: Mini_Batch_Gradient_Descent}.
-\begin{algorithm}
-	\label{alg: Mini_Batch_Gradient_Descent}
-	\caption{Mini Batch Gradient Descent}
-	\KwIn{Training Dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, learning rate $\eta $, max iteration $ N$, parameter $W$}
-	\KwOut{Optimized parameter $\hat{W}$}
-	$t \gets 1$ \\
-	\For{$t < N $}
-	{
-		$ i \gets 0 $ \\
-		\For{$ X_{batch}, y_{batch} $ in $D$}
-		{
-			$\hat{y}_{batch} \gets X^{T}_{batch}W $ \\
-			$ L(\hat{y}_{batch}, y_{batch}) \gets \frac{1}{2}(\hat{y}_{batch} - y_{batch})^{T}(\hat{y}_{batch} - y_{batch})$ \\
-			$\Delta{W} \gets \frac{\partial L}{\partial W}$ \\
-			$W \gets W - \eta * \Delta{W}$ \\
-		}
-	}
-	$\hat{W} \gets W$ \\
-	return $\hat{W}$
-\end{algorithm}
+So \par
+\begin{equation}
+	\label{eqa:hinge_loss}
+	\xi_i = max(0, 1 - y_i(w^Tx_i + b))
+\end{equation} \par
+Equation~\ref{eqa:hinge_loss} is the Hinge Loss (HL). Finally the optimization problem for SVM becomes
+\begin{equation}
+\label{eqa:svm_final_optimization}
+min_{w, b}~\frac{w^Tw}{2} + \frac{C}{m}\Sigma_{i=1}^m \max(0, 1 - y_i(w^Tx_i + b))
+\end{equation} \par
+We do a small modification for Equation~\ref{eqa:svm_final_optimization}, so that we can see the role of $C$ in SVM.
+\begin{equation}
+	\begin{aligned}
+	min_{w, b}~\lambda w^Tw + \frac{1}{m}\Sigma_{i=1}^m \max(0, 1 - y_i(w^Tx_i + b)) \\
+	where~\lambda = \frac{1}{2C}
+	\end{aligned}
+\end{equation} \par
+Here, we can see that $\lambda$ e.g. $\frac{1}{2C}$ is the regularizer, like Ridge Regression (RR). So, the magnitude of $W$ is in direct proportion to $C$.
 
@@
 \subsection{Dataset}
-We conduct all the experiments on housing dataset, which has total 506 examples and each example's form is $(x, y)$, where $x \in \mathbf{R}^{13}$ and $y \in \mathbf{R}$.
-We split the dataset into three part: 272 training examples, 67 validation examples and 167 test examples.
-$X$ is already scaled between $-1$ and $1$.
-And we normalized the $X_{train}, X_{val}, X_{test} $ by using the mean and variance of $X_{train}$.
+We conduct all the experiments on a9a dataset, which has total 48842 examples and each example's form is $(x, y)$, where $x \in \mathbf{R}^{123}$ and $y \in \{0, 1\}~(in~LR)~and~\{-1, +1\}~(in~SVM)$.
+We split the dataset into three part: 26049 training examples, 6512 validation examples and 16281 test examples.
+We normalized the $X_{train}, X_{val}, X_{test} $ by using the mean and variance of $X_{train}$.
 
 \subsection{Implementation}
-We implement the LR, RR and GD, GD, MBGD algorithm using python and mainly rely on the numpy package.
+We implement the LR, SVM, optimizers, initilizers and loss functions using python and mainly rely on the numpy package.
 
-\subsection{Linear Regression and Ridge Regression}
-In this section, we conduct the experiment of serveral magnitude of $\lambda$ of RR in training set, which leads to serveral $W_{ridge}$.
-We use $L_2{norm}$ to represent the magnitude of a vector.
-Given $v \in \mathbf{R}^{n}$
-\begin{equation}
-	L_2norm(v) = \sqrt{\Sigma_{i=1}^{n} v_{i}}
-\end{equation} \par
-From Table~\ref{tab:Ridge_Regression}, we can see that: \par
-First, as the magnitude of lambda becomes bigger, both $MSE_{train}$ and $MSE_{val}$ become bigger. \par
-Second, as the magnitude of lambda becomes bigger, the magnitude of $W_{ridge}$ become smaller. \par
-The first observation is not often the cases. But the second observation can be explained that as the regularizer $\lambda$ become bigger, the $W$ is regularized, so that it is smaller. \par
-By comparing Table~\ref{tab:Ridge_Regression} and Table~\ref{tab:Linear_Regression}, we can see that, the performance and the weight magnitude is almost the same as the $\lambda$ is small, but the difference become larger as $\lambda$ grows.
+\subsection{Hyper-parameter C in SVM}
+In this section, we explore the influence of C in SVM.
+We set $log_{10}^{C}$ in a coarse-grained range e.g.
+-2, -1, 0, 1, 2, 3, 4, and compare $loss_{train}$, $loss_{val}$, $accuracy_{train}$, $accuracy_{train}$ and $l_2norm$ of $w$, where $loss =  \frac{w^Tw}{2} + \frac{C}{m}\Sigma_{i=1}^m \max(0, 1 - y_i(w^Tx_i + b))$ and $ l_2norm(w) = \sqrt{\Sigma_{i=1}^n w_i}$.
+We zero initilize $w$ and $b$, use SGD as optimizer with learning rate 0.001, set epoch to 200 and batch size to 64.
 \par
-We also explore the weight mantitude between LR and RR under different $\lambda$ magnitude setting.
-Specifically, we set $log_{10}^{\lambda}$ in range from -7 to 3.
-We can see from Fig~\ref{fig:ridge_w}, as the magnitude of $\lambda$ growing, the weight magnitude of ridge regression become much smaller than linear regression.
+From Fig~\ref{fig:C_loss}, we can see that, when $C$ is very small, e.g.
+smaller than 1, the gradient descent process is very unstable and the loss is higher than other.
+As $C$ goes up, the loss decreases, e.g.
+from 1 to 10.
+But when $C$ gets larger than 10, the loss become slightly bigger, but still better than small $C$, like 0.01 and 0.1.
+So, we can draw the conclusion that, bigger $C$ usually better than small $C$, and the best C is in the middle, which is not very big but also not very small.
+As we can see from Fig~\ref{fig:C_loss}, $C = 10$ gets the lowest loss.
 \par
+From Fig~\ref{fig:C_acc}, we can see that, when $C$ is very small, e.g.
+0.01, the accracy in both training set and validation set is much lower than others.
+Small $C$ like 0.01 and 0.1 get worse performance comparing with others.
+In training set, the accracy is very similar when $C$ bigger than 1.
+In validation set, $C = 10$ gets slightly better performance comparing with others.
+Best validation performance under each $C$ setting can be found in Table~\ref{tab:C_performance}.
+\par
+From Fig~\ref{fig:c_mag}, we can see that, as $C$ goes up, $l_2norm(w)$ goes up except $C = 100$.
+As said above, $\frac{1}{2C}$ can be viewed as regurilizer, so when $C$ is bigger, the smaller of its impact on regurization, so the weight maginitude goes up.
+\begin{figure*}[!hbt]
+	\centering
+	\subfigure[$Loss_{train}$ under different $C$.] {\includegraphics[width=\columnwidth]{c_train_loss}}
+	\subfigure[$Loss_{val}$ under different $C$.] {\includegraphics[width=\columnwidth]{c_val_loss}}
+	\caption{ $Loss_{train}~and~Loss_{val}$ under different $C$. }
+	\centering
+	\label{fig:C_loss}
+\end{figure*} \par
+
+\begin{figure*}[!hbt]
+	\centering
+	\subfigure[$Accuracy_{train}$ under different $C$.] {\includegraphics[width=\columnwidth]{c_train_acc}}
+	\subfigure[$Accuracy_{val}$ under different $C$.] {\includegraphics[width=\columnwidth]{c_val_acc}}
+	\caption{ $Accuracy_{train}~and~Accuracy_{val}$ under different $C$. }
+	\centering
+	\label{fig:C_acc}
+\end{figure*} \par
+
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{c_magnitude}
+		% Create a subtitle for the figure.
+		\caption{The magnitude of $W$ under different $C$.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:c_mag}
+	\end{center}
+\end{figure} \par
+
 \begin{table}[!hbt]
@@
 		% Title of the table
-		\caption{Different lambdas' impact in terms of error and $W$ magnitude. Best result are in bold.}
-		\label{tab:Ridge_Regression}
+		\caption{Best Result in Validation set under different C's settings. Best result are in bold.}
+		\label{tab:C_performance}
 		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
@@
 			% For a linebreak type \\
-			$log_{10}^{\lambda}$ & -2 & -1 & 0 & 1 & 2 & 3 \\
+			$log_{10}^{C}$ & -2 & -1 & 0 & 1 & 2 & 3 & 3 \\
 			\hline
-			$MSE_{train}$   & \textbf{10.23} & \textbf{10.23} & 10.24 & 10.63 & 30.37 & 181.35   \\
+			$Accuracy_{val}$   & 84.39 & 84.42 & 84.72 & \textbf{84.75} & 84.73 & 84.56 & 84.49   \\
 			\hline
-			$MSE_{val}$  & \textbf{17.08} & 17.09 & 17.16 & 18.20 & 43.92 & 214.55   \\
-			\hline
-			$L_2norm(W_{ridge})$  & 0.83 & 0.82 & 0.81 & 0.72 & 0.50 & 0.38 \\
+			$Epoch$  & \textbf{2} & 86 & 62 & 138 & 173 & 147 & 145   \\
 			\hline
@@
 
-\begin{table}[!hbt]
-	% Center the table
+\subsection{Loss function comparision in SVM}
+In this section, we conduct experiment on loss function comparision in SVM.
+Especially, we compare two loss function, hinge loss which is illustrated above And Exponential Loss (EL), where $EL = exp\{-y_i(w^Tx_i + b)\}$.
+More formaly, $HL(z) = max(0, 1 - z)$ and $EL(z) = exp^{-z}$.
+Fig~\ref{fig:loss_fn} shows that HL and EL both have one advantage and one disadvantage.
+HL is stable when z is very mall, however EL become very large, which will lead to numeric unstable.
+EL is derivable every but HL is not derivable when $z = 1$.
+We use SGD as optimizer with learning rate 0.001, set epoch to 200, batch size to 64 and C to 10.\par
+From Fig~\ref{fig:l_val_loss} and Fig~\ref{fig:l_val_acc}, we can see that the performance of HL is superior. EL has numeric unstablity problem during gradient descent process. \par
+\begin{figure}[!hbt]
+	% Center the figure.
 	\begin{center}
-		% Title of the table
-		\caption{Linear Regression Error and $W$ magnitude.}
-		\label{tab:Linear_Regression}
-		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
-		\begin{tabular}{|c|c|}
-			% To create a horizontal line, type \hline
-			\hline
-			$MSE_{train}$ & 10.23    \\
-			\hline
-			$MSE_{val}$ & 17.08    \\
-			\hline
-			$L_2norm(W)$ & 0.83  \\
-			\hline
-		\end{tabular}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{loss_fn}
+		% Create a subtitle for the figure.
+		\caption{The plot of HL and EL.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:loss_fn}
 	\end{center}
-\end{table}
+\end{figure} \par
 
@@
 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{ridge_w}
+		\includegraphics[width=\columnwidth]{l_val_loss}
 		% Create a subtitle for the figure.
-		\caption{The magnitude of $W_{ridge}$ under different lambda mgnitude.}
+		\caption{$loss_{val}$ under different loss function.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:ridge_w}
+		\label{fig:l_val_loss}
 	\end{center}
-\end{figure}
-
-\subsection{Gradient Descent, Stochastic Gradient Descent and Mini Batch Gradient Descent}
-In this section, we conduct experiments on optimizing the LR model by using GD, SGD, MBGD  algorrithms, and compare them in terms of convergence and time cost. \par
-We first evaluate the convergence of three algorithms, specificlly we set batch size in a range from 1 to number of full examples in training set.
-When the batch size is one, mini batch gradient descent becomes stochastic gradient descent and when the batch size equals to number of full examples, mini batch gradient descent becomes gradient descent.
-All experiments are with the same learning rate 0.01.\par
-As we can see from Fig~\ref{fig:batch_size_train} and Fig~\ref{fig:batch_size_val}, as the batch size become larger, the convergence of the linear regression model bocome slower.
-The reason is that, in each epoch, the smaller the batch size, the model have more update steps, so the convergence is faster.
-Especially, the stochastic gradient descent converges within 10 steps, while gradient descent requires nearly 400 steps, there is a 400x margin.\par
-We then measure the time cost for each batch size. \par 
-As illustrated in Fig~\ref{fig:time_cost}, the smaller the batch size, more time cost is required, because of the explicit for loop in the SGD and MBGD.
-Especially, the GD requires only about 1 seconds in one step, while SGD requires 60 seconds, there exist a 60x margin.
-\par
-% This is how you include a eps figure in your document. LaTeX only accepts EPS or TIFF files.
-\begin{figure}[!hbt]
-	% Center the figure.
-	\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{batch_size_train}
-		% Create a subtitle for the figure.
-		\caption{The $MSE$ of training set under different batch size.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:batch_size_train}
-	\end{center}
-\end{figure}
+\end{figure} \par
 
@@
 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{batch_size_val}
+		\includegraphics[width=\columnwidth]{l_val_acc}
 		% Create a subtitle for the figure.
-		\caption{The $MSE$ of validation set under different batch size.}
+		\caption{$Accuracy_{val}$ under different loss function.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:batch_size_val}
+		\label{fig:l_val_acc}
 	\end{center}
-\end{figure}
+\end{figure} \par
+
+\subsection{Initilizer comparision in both LR and SVM}
+In this section, we compare the performance of LR and SVM under different initilizers.
+We explore over ones, zeros, xavier uniform and random initializer.
+Ones initilizers makes the initial $w$ to all one and Zeros initilizers makes the initial $w$ to all zero.
+Xavier uniform initializer uniformally initial $w$, but bounded to interval $[-n, n]$, where $n$ is $W$'s dimension.
+Random initializer initial $w$ from standard normal distribution.
+We use SGD as optimizer with learning rate 0.001, set epoch to 200, batch size to 64 and C to 10 in SVM.
+We use HL as SVM's loss function and BCE as LR's loss function.\par
+From Fig~\ref{fig:lr_init_val_loss} and Fig~\ref{fig:lr_init_val_acc}, we can see that LR's performance is affected by the initilizer.
+Typically Ones initilizer brings the worst performance and Xavier uniform initializer bring the best performance.
+\par
+From Fig~\ref{fig:svm_init_val_loss} and Fig~\ref{fig:svm_init_val_acc}, we can see that SVM is very robust to the initilizer, different initilizer didn't disturb the performance. \par
 
@@
 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{time_cost}
+		\includegraphics[width=\columnwidth]{lr_init_val_loss}
 		% Create a subtitle for the figure.
-		\caption{The time cost of 100 epoches under different batch size.}
+		\caption{LR's $BCE_{val}$ under different initilizer.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:time_cost}
+		\label{fig:lr_init_val_loss}
 	\end{center}
-\end{figure}
-
-\subsection{Impact of learning rate}
-In this section, we evaluate the impact of learning rate in MBGD, we set batch size to 64 and epochs to 200. We set learning rate in a range e.g. 1e-4, 1e-3, 1e-2, 1e-1, 1. \par
-As presented in Fig~\ref{fig:lr_train} and Fig~\ref{fig:lr_val}, small learning rate tends to make the convergence smoothly, but needs more epoches to fully converge.
-However, big learning rate make the convergence very fast, but will not guarateee that the convergence will be near the optimal(or local optimal) and makes the $MSE$ shaking around after a specific epoch.
-\par
+\end{figure} \par
 
@@
 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{lr_train}
+		\includegraphics[width=\columnwidth]{lr_init_val_acc}
 		% Create a subtitle for the figure.
-		\caption{The $MSE$ in training set under different learning rate.}
+		\caption{LR's $Accuracy_{val}$ under different initilizer.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:lr_train}
+		\label{fig:lr_init_val_acc}
 	\end{center}
-\end{figure}
+\end{figure} \par
 
@@
 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{lr_val}
+		\includegraphics[width=\columnwidth]{svm_init_val_loss}
 		% Create a subtitle for the figure.
-		\caption{The $MSE$ in validation set under different learning rate.}
+		\caption{SVM's $HL_{val}$ under different initilizer.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:lr_val}
+		\label{fig:svm_init_val_loss}
 	\end{center}
-\end{figure}
-
-\subsection{Weight magnitude between CSF and MBGD}
-In this section, we explore the weight magnitude($L_2norm$) between CSF and MBGD optimized weight of linear regression. \par
-
-Then, we experiments on comparing the weight magnitude of CFS and MBGD optimized LR.
-In MBGD, we set learning rate to 0.01 and batch size to 64.
-We can see that MBGD optimized LR's weight magnitude is stable after some epoches.
-But MBGD optimized weight's magnitude has a large margin(e.g.
-about 0.6) to CFS optimized weight.
-The reason is still unclear.
-\par
+\end{figure} \par
 
@@
 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{mbgd_w}
+		\includegraphics[width=\columnwidth]{svm_init_val_acc}
 		% Create a subtitle for the figure.
-		\caption{The magnitude of $W_{mbgd}$ under different epoches..}
+		\caption{SVM's $Accuracy_{val}$ under different initilizer.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:mbgd_w}
+		\label{fig:svm_init_val_acc}
 	\end{center}
-\end{figure}
-
-\subsection{Performance} 
-In this section, we report the performance on CFS optimized LR, RR and MBGD optimized LR in training set, validation set and test set.
-The $\lambda$ is set to 1e-7 after validation.
-And batch size is set to 64 in MBGD, learing rate set to 0.01 and epoch set to 200 by validation.
-\par
-From Table~\ref{tab:Performance}, we can see that alougth MBGD optimized LR's $MSE_{train}$ and $MSE_{val}$ are not the best, but its result in $MSE_{test}$ is outstanding.
-The reason remains unclear, maybe the same reason that the magnitude between CFS optimized LR and MBGD optimized LR has a large margin.
-\par
-\begin{table}[!hbt]
-	% Center the table
-	\begin{center}
-		% Title of the table
-		\caption{Final Performance of CFS optimized LR, RR and MBGD optimized LR, best result are in bold.}
-		\label{tab:Performance}
-		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
-		\begin{tabular}{|c|c|c|c|}
-			% To create a horizontal line, type \hline
-			\hline
-			% To end a column type &
-			% For a linebreak type \\
-			& LR & RR & MBGD \\
-			\hline
-			$MSE_{train}$   & \textbf{10.23} & \textbf{10.23} & 11.37   \\
-			\hline
-			$MSE_{val}$  & \textbf{17.08} & \textbf{17.08} & 19.04   \\
-			\hline
-			$MSE_{test}$  & 10.20 &  10.20 & \textbf{10.14}  \\
-			\hline
-		\end{tabular}
-	\end{center}
-\end{table}
+\end{figure} \par
 

### 2019-11-11 simple_ml/example/exp2.py

@@ -7,7 +7,7 @@ from simple_ml.utils.distance import euclidean
 from simple_ml.preprocessing.general import Standardizer
 from simple_ml.nn.layer import Input, Linear, Dropout, Softmax
 from simple_ml.nn.model import Model
-from simple_ml.nn.initializer import zeros, ones
+from simple_ml.nn.initializer import zeros, ones, default_weight_initializer
 from simple_ml.nn.regularizer import L2_Regularizer, L1_Regularizer, L1L2_Regularizer
 from simple_ml.nn.optimizer import SGD, Momentum, Adam, RMSProp
 from simple_ml.utils.metric import accuracy, absolute_error, square_error
@@ -109,6 +109,8 @@ def svm():
     #            # regularizer=L1L2_Regularizer(l2=1),
     #            activation='swish')(X)
     X = Linear(output_dim=1,
+               # initializer='default_weight_initializer',
+               initializer=default_weight_initializer,
                regularizer=L2_Regularizer(1e-5),
                # regularizer=L1_Regularizer(1e-2),
                # regularizer=L1L2_Regularizer(l2=1),
@@ -117,7 +119,7 @@ def svm():
     # model.compile('HL', optimizer=SGD(lr=0.001))
     model.compile('HL', optimizer=Adam(lr=0.001))
     model.fit(X_train, y_train,
-              verbose=10, epochs=1000,
+              verbose=10, epochs=100,
               validation_data=(X_test, y_test),
               batch_size=64, metric='svm_binary_accuracy',
               shuffle=True,

### 2019-11-11 simple_ml/nn/initializer.py

@@ -25,7 +25,9 @@ glorot_uniform_initializer = xavier_uniform_initializer
 
 
 def default_weight_initializer(shape):
-    return np.random.randn(shape) / np.sqrt(shape[1])
+    m = shape[0]
+    n = shape[1] if len(shape) > 1 else shape[0]
+    return np.random.randn(m, n) / np.sqrt(n)
 
 
 def zeros(shape):
@@ -42,6 +44,7 @@ _initializer_map = {
     'default_weight_initializer': default_weight_initializer,
     'zeros': zeros,
     'ones': ones,
+    'random': default_weight_initializer,
 }
 
 

### 2019-11-11 simple_ml/nn/layer.py

@@ -1,6 +1,7 @@
 import numpy as np
 from .activation import get_activation
 from .regularizer import get_regularizer
+from .initializer import get_initializer
 from .initializer import xavier_uniform_initializer
 from .utils import conv_forward_im2col, conv_backward_im2col
 from .utils import max_pool_forward_fast, max_pool_backward_fast
@@ -176,7 +177,7 @@ class Linear(Layer):
         self.output_dim = output_dim
         self.regularizer = get_regularizer(regularizer)
         self.activation = get_activation(activation)
-        self.initializer = initializer
+        self.initializer = get_initializer(initializer)
         self.input_shape = None
         self.output_shape = None
         if self.input_dim is not None:
@@ -466,7 +467,7 @@ class Conv2d(Layer):
         self.output_shape = None
         self.padding = padding
         self.activation = get_activation(activation)
-        self.initializer = initializer
+        self.initializer = get_initializer(initializer)
         self.stride = stride
         if self.input_shape is not None:
             self.connection(None)

### 2019-11-11 simple_ml/nn/loss.py

@@ -155,7 +155,7 @@ class HingeLoss(Loss):
 
 class ExponentialLoss(Loss):
     """
-    A proximation to hinge loss.
+    A approximation to hinge loss.
     # for now, it is not stable.
     """
 
@@ -182,7 +182,7 @@ hl = HL = HingeLoss
 el = EL = ExponentialLoss
 
 cut_off = 1e-12
-chop_off = 5
+chop_off = 3
 
 
 def _cut_off(z):

### 2019-11-11 simple_ml/nn/model.py

@@ -62,6 +62,40 @@ class Module(object):
             return []
         return self.valid_metrics[self.metric]
 
+    def best_performance(self):
+        performance = {}
+        key = 'train_set'
+        tr_metrics = np.array(self.training_metrics[self.metric])
+        best_epoch = tr_metrics.argmax()
+        best_metric = tr_metrics[best_epoch]
+        best_loss = self.training_losses[best_epoch]
+        performance[key] = {
+            'best_epoch': best_epoch,
+            'best_metric': best_metric,
+            'best_loss': best_loss,
+        }
+
+        key = 'val_set'
+        if len(self.validation_metrics) == 0:
+            performance[key] = {
+                'best_epoch': None,
+                'best_metric': None,
+                'best_loss': None,
+            }
+
+        else:
+            val_metrics = np.array(self.valid_metrics[self.metric])
+            best_epoch = val_metrics.argmax()
+            best_metric = val_metrics[best_epoch]
+            best_loss = self.valid_losses[best_epoch]
+            performance[key] = {
+                'best_epoch': best_epoch,
+                'best_metric': best_metric,
+                'best_loss': best_loss,
+            }
+
+        return performance
+
     def compile(self, loss, optimizer='sgd'):
         """Configures the model for training.
         # Arguments
@@ -77,10 +111,16 @@ class Module(object):
             ValueError: In case of invalid arguments for
                 `optimizer`, `loss`.
         """
+        self.set_loss(loss)
+        self.set_optimizer(optimizer)
+
+    def set_loss(self, loss):
         loss = loss or None
+        self.loss = get_loss(loss)
+
+    def set_optimizer(self, optimizer):
         optimizer = optimizer or None
         self.optimizer = get_optimizer(optimizer)
-        self.loss = get_loss(loss)
 
     def peak(self, X, y, peek_type, set_type, num_show=5):
         allow_set_types = ['train', 'valid']

### 2019-11-11 simple_ml/utils/metric.py

@@ -31,7 +31,7 @@ def svm_binary_accuracy(outputs, targets):
     # print(targets.shape, 'targets')
     # print(np.sum(acc, axis=0).shape, 'np.sum(acc, axis=0)')
     # print(acc.shape, 'np.sum(acc, axis=0)')
-    return np.sum(acc, axis=0)
+    return np.sum(acc, axis=0).squeeze()
 
 
 def accuracy(outputs, targets):

### 2019-11-11 simple_ml/example/report2/paper.tex
partial complete report2.

@@
 We set $log_{10}^{C}$ in a coarse-grained range e.g.
--2, -1, 0, 1, 2, 3, 4, and compare $loss_{train}$, $loss_{val}$, $accuracy_{train}$, $accuracy_{train}$ and $l_2norm$ of $w$, where $loss =  \frac{w^Tw}{2} + \frac{C}{m}\Sigma_{i=1}^m \max(0, 1 - y_i(w^Tx_i + b))$ and $ l_2norm(w) = \sqrt{\Sigma_{i=1}^n w_i}$.
+-2, -1, 0, 1, 2, 3, 4, and compare $loss_{val}$,  $accuracy_{val}$ and $l_2norm$ of $w$, where $loss =  \frac{w^Tw}{2} + \frac{C}{m}\Sigma_{i=1}^m \max(0, 1 - y_i(w^Tx_i + b))$ and $ l_2norm(w) = \sqrt{\Sigma_{i=1}^n w_i}$.
 We zero initilize $w$ and $b$, use SGD as optimizer with learning rate 0.001, set epoch to 200 and batch size to 64.
@@
 As said above, $\frac{1}{2C}$ can be viewed as regurilizer, so when $C$ is bigger, the smaller of its impact on regurization, so the weight maginitude goes up.
-\begin{figure*}[!hbt]
-	\centering
-	\subfigure[$Loss_{train}$ under different $C$.] {\includegraphics[width=\columnwidth]{c_train_loss}}
-	\subfigure[$Loss_{val}$ under different $C$.] {\includegraphics[width=\columnwidth]{c_val_loss}}
-	\caption{ $Loss_{train}~and~Loss_{val}$ under different $C$. }
-	\centering
+\par
+
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{c_val_loss}
+		% Create a subtitle for the figure.
+		\caption{$Loss_{val}$ under different $C$.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
 		\label{fig:C_loss}
-\end{figure*} \par
+	\end{center}
+\end{figure} \par
 
-\begin{figure*}[!hbt]
-	\centering
-	\subfigure[$Accuracy_{train}$ under different $C$.] {\includegraphics[width=\columnwidth]{c_train_acc}}
-	\subfigure[$Accuracy_{val}$ under different $C$.] {\includegraphics[width=\columnwidth]{c_val_acc}}
-	\caption{ $Accuracy_{train}~and~Accuracy_{val}$ under different $C$. }
-	\centering
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{c_val_acc}
+		% Create a subtitle for the figure.
+		\caption{$Accuracy_{val}$ under different $C$.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
 		\label{fig:C_acc}
-\end{figure*} \par
+	\end{center}
+\end{figure} \par
 
@@
 	\end{center}
-\end{table}
+\end{table} \par
 
@@
 
+\subsection{Optimizer comparision in both LR and SVM}
+In this section, we compare the performance of LR and SVM with different optimizers.
+We explore over Stochastic Gradient Descent (SGD), Momentum, Adam and RMSProp.
+We use xavier uniform initializer, set learning rate to 0.001 epoch to 200, batch size to 64 and C to 10 in SVM.
+We use HL as SVM's loss function and BCE as LR's loss function.\par
+From Fig~\ref{fig:lr_optim_val_loss} and Fig~\ref{fig:lr_optim_val_acc}, we can see that LR's performance is affected by the optimizer.
+Typically SGD converges very slowly; Momentum converges faster than SGD, but not as good as SGD's performance; both Adam and RMSProp converge very fast and get to the best performance.\par
+From Fig~\ref{fig:svm_optim_val_loss} and Fig~\ref{fig:svm_optim_val_acc}, we can see that SVM is very robust to the optimizer too, different optimizer didn't disturb the performance except Momentum which converges slower and get worse performance comparing with other optimizers.
+\par
+
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{lr_optim_val_loss}
+		% Create a subtitle for the figure.
+		\caption{LR's $BCE_{val}$ under different optimizer.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:lr_optim_val_loss}
+	\end{center}
+\end{figure} \par
+
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{lr_optim_val_acc}
+		% Create a subtitle for the figure.
+		\caption{LR's $Accuracy_{val}$ under different optimizer.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:lr_optim_val_acc}
+	\end{center}
+\end{figure} \par
+
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{svm_optim_val_loss}
+		% Create a subtitle for the figure.
+		\caption{SVM's $HL_{val}$ under different optimizer.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:svm_optim_val_loss}
+	\end{center}
+\end{figure} \par
+
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{svm_optim_val_acc}
+		% Create a subtitle for the figure.
+		\caption{SVM's $Accuracy_{val}$ under different optimizer.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:svm_optim_val_acc}
+	\end{center}
+\end{figure} \par
+
 \section{Conclusion}

### 2019-11-12 simple_ml/example/report2/paper.tex
complete report2.

@@
 2. Loss function comparision in SVM. \\
-3. Initilizer comparision in both LR and SVM. \\
+3. initializer comparision in both LR and SVM. \\
 4. Optimizer comparision in both LR and SVM. \\
@@
 These two algorithms are classic, so we fully explore them by solving a9a binary classification task.
-Beyond that, we will explore the initilizer and optimizer selection in both LR and SVM.
+Beyond that, we will explore the initializer and optimizer selection in both LR and SVM.
 
@@
 \subsection{Implementation}
-We implement the LR, SVM, optimizers, initilizers and loss functions using python and mainly rely on the numpy package.
+We implement the LR, SVM, optimizers, initializers and loss functions using python and mainly rely on the numpy package.
 
@@
 
-\subsection{Initilizer comparision in both LR and SVM}
-In this section, we compare the performance of LR and SVM under different initilizers.
+\subsection{initializer comparision in both LR and SVM}
+In this section, we compare the performance of LR and SVM under different initializers.
 We explore over ones, zeros, xavier uniform and random initializer.
-Ones initilizers makes the initial $w$ to all one and Zeros initilizers makes the initial $w$ to all zero.
+Ones initializers makes the initial $w$ to all one and Zeros initializers makes the initial $w$ to all zero.
 Xavier uniform initializer uniformally initial $w$, but bounded to interval $[-n, n]$, where $n$ is $W$'s dimension.
@@
 We use HL as SVM's loss function and BCE as LR's loss function.\par
-From Fig~\ref{fig:lr_init_val_loss} and Fig~\ref{fig:lr_init_val_acc}, we can see that LR's performance is affected by the initilizer.
-Typically Ones initilizer brings the worst performance and Xavier uniform initializer bring the best performance.
+From Fig~\ref{fig:lr_init_val_loss} and Fig~\ref{fig:lr_init_val_acc}, we can see that LR's performance is affected by the initializer.
+Typically Ones initializer brings the worst performance and Xavier uniform initializer bring the best performance.
 \par
-From Fig~\ref{fig:svm_init_val_loss} and Fig~\ref{fig:svm_init_val_acc}, we can see that SVM is very robust to the initilizer, different initilizer didn't disturb the performance. \par
+From Fig~\ref{fig:svm_init_val_loss} and Fig~\ref{fig:svm_init_val_acc}, we can see that SVM is very robust to the initializer, different initializer doesn't disturb the performance. \par
 
@@
 		% Create a subtitle for the figure.
-		\caption{LR's $BCE_{val}$ under different initilizer.}
+		\caption{LR's $BCE_{val}$ under different initializer.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
@@
 		% Create a subtitle for the figure.
-		\caption{LR's $Accuracy_{val}$ under different initilizer.}
+		\caption{LR's $Accuracy_{val}$ under different initializer.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
@@
 		% Create a subtitle for the figure.
-		\caption{SVM's $HL_{val}$ under different initilizer.}
+		\caption{SVM's $HL_{val}$ under different initializer.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
@@
 		% Create a subtitle for the figure.
-		\caption{SVM's $Accuracy_{val}$ under different initilizer.}
+		\caption{SVM's $Accuracy_{val}$ under different initializer.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
@@
 
+\subsection{Performance on validation set and test set.}
+Now we report the final performance of LR and SVM on test set.
+For LR, we set optimizer to Adam with learning rate 0.001, batch size to 64, initializer to Xavir uniform intitializer, epoch to 200.
+For SVM, we set optimizer to Adam with learning rate 0.001, batch size to 64, initializer to Xavir uniform initializer, $C$ to 10, epoch to 200.
+\par
+Although LR is very sensitive to initializer and optimizer, but using the best initializer Xavir uniform initializer and optimizer Adam, it outperform SVM by a little under the same experiment settings and enjoys faster convergence.
+\par
+
+\begin{table}[!hbt]
+	% Center the table
+	\begin{center}
+		% Title of the table
+		\caption{Result on a9a validation set and test set. Best result are in bold.}
+		\label{tab:final_performance}
+		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
+		\begin{tabular}{|c|c|c|}
+			% To create a horizontal line, type \hline
+			\hline
+			% To end a column type &
+			% For a linebreak type \\
+			& LR & SVM \\
+			\hline
+			$Accuracy_{val}$   & \textbf{84.66} & 84.44   \\
+			\hline
+			$Accuracy_{test}$   & \textbf{84.98} & 84.88   \\
+			\hline
+			$Epoch$  & \textbf{37} & 107   \\
+			\hline
+		\end{tabular}
+	\end{center}
+\end{table} \par
+
 \section{Conclusion}
-In this report, we explore the CFS optimized LR, CFS optimized RR and MBGD optimized LR.
-We conduct the experiments on the CFS optimized LR and RR in terms of performance and weight magnitude.
-We also explore GD, SGD, MBGD in terms of convergence and time efficiency.
-Moreover, we tuning the hyper-parameter learning rate in MBGD.
-We also compare the weight magnitude between CFS optimized LR and MBGD optimized LR.
-Finally, we report the performance in CFS optimized LR, RR and MBGD LR.
-After a series of experiments, we now get more insight of LR, RR and GD and its variants SGD and MBGD.
-\par
+In this report, we explore SVM and logistic regression.
+Specifically, we explore the hyper-parameter $C$ and loss function comparision in SVM, we draw the conclusion that best $C$ is something in the middle (not too small and too big) and hinge loss is better than exponential loss.
+Besides that, we also compare different initializers and optimizers in logistic regression.
+We oberseve that SVM is more robust than logistic regression under differen initializer and optimizer settings; Adam and RMSProp both obtain very good performance in logistic regression and SVM.
+Finally, we report te performance of LR and SVM under each best settings and get their performance on test set, suprisingly LR outperform SVM in a little performance.\par
 

### 2019-11-12 setup.py
complete exp2.

@@ -2,7 +2,7 @@ from setuptools import setup, find_packages
 
 setup(
     name='pip_setup',
-    version='0.1.1',
+    version='0.1.2',
     description='simple: simple machine learning framework.',
     classifiers=[
         'License :: OSI Approved :: MIT License',

### 2019-11-12 simple_ml/example/report3/paper.tex
add report3.

--- 2019-11-12 simple_ml/example/report2/paper.tex
@@
 
+\usepackage{mathbbol}
 \makeatletter
@@
 % Define document title and author
-	\title{Logistic Regression and SVM}
+	\title{Adaboost for face image classification}
 	\maketitle
@@
 \begin{abstract}
-In this report, we solve the binary classification problem in a9a dataset by Logistic Regression (LR) and Support Vector Machine (SVM). \\
-We perform experiments on four aspects: \\
-1. Hyper-parameter tuning in SVM. \\
-2. Loss function comparision in SVM. \\
-3. initializer comparision in both LR and SVM. \\
-4. Optimizer comparision in both LR and SVM. \\
+In this report, we solve the face/non-face classification problem by adaboost with Decision Tree Classifier (DTC) as weak learner. \\
+We perform experiments on three aspects: \\
+1. Weak learner's performance effect. \\
+2. Number of weak learner's exploration. \\
 \end{abstract}
@@
 	% \PARstart{}{} creates a tall first letter for this first paragraph
-\PARstart{L}{ogistic} Regression(LR) is an extension of linear regression, which use $\sigma$ function as activation to map the output of linear regression into a interval (0, 1).
-So that LR can output the probability in binary classification.
-SVM is also an extension of linear regression.
-Based on the idea "large margin classification", SVM can perform very well in many classification task.
-Even now, LR and SVM are widely used in academic and industry community.
-These two algorithms are classic, so we fully explore them by solving a9a binary classification task.
-Beyond that, we will explore the initializer and optimizer selection in both LR and SVM.
+\PARstart{A}{daboost} short for "Adaptive Boosting",  is an ensemble method that combine a bunch of weak learners into a strong learner which outperforms all the weak learners.
+It's wildly used in academic and industry community, which make it very important for us to fully explore it.
+We will explore the the effect of weak learner's performance and the performance with different number of weak learner.
 
@@
 \section{Methods and Theory}
-In this part, we first define logistic regression and LR's loss function Binary Cross Entrophy (BCE). Then we define SVM and SVM's loss function Hinge Loss (HL).
-\subsection{Logistic Regression}
-Given dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, where $x_{i} \in \mathbf{R}^{n}$ and $y_{i} \in \{0, 1\}$. Mathematically, for a single training datapoint $(x, y)$, LR assumes: \par
- \begin{center}
-	\begin{equation}
-	P(Y = 1|X = x) = \sigma(z) 
-	\end{equation}
-	\begin{equation}
-	P(Y = 0|X = x) = 1 - \sigma(z)
-	\end{equation}
-	\begin{equation}
-	z = F(x; W)
-	\end{equation}
-\end{center} \par
-where $F(x; W)$ is linear regression parameterized by $W$ and $\sigma(.)$ is sigmoid function, where $\sigma(z) = \frac{1}{1 + e^{-z}} \in (0, 1)$.
-\subsection{Binary Cross Entrophy}
-Logistic regression assumes that each datapoint is independent, so the likelihood of all data is: \par
-\begin{equation}
-	\begin{aligned}
-	L(W) &= \prod_{i=1}^m P(Y = y_i | X = x_i) \\ &= \prod_{i=1}^m \sigma(z)^{y_i} (1 - \sigma(z)^{1 - y_i} )
-	\end{aligned}
-\end{equation} \par
+In this part, we define Adaboost algorithm.
+\subsection{Adaboost}
+Given dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, where $x_{i} \in \mathbf{R}^{n}$.
+$y_{i} \in \{-1, 1\}$ and weak Learner $L(x) \in \{-1, 1\} $, Adaboost algorithm can be found in Algorithm~\ref{alg:adaboost}.
+\par
 
-So our goal is to maximize the likelihood of data, in practice we maximize the log likelihood. \par
-\begin{equation}
-\begin{aligned}
-LL(W) &= log\prod_{i=1}^m \sigma(z)^{y_i} (1 - \sigma(z)^{1 - y_i} ) \\ &= \Sigma_{i=1}^{m} (y_i \sigma(z) + (1 - y_i)(1 - \sigma(z)))
-\end{aligned}
-\end{equation} \par
-When using mini batch gradient descent (MBGD) algorithm, we want to minimize something, so we minimize the negative log likelihood. \par
+\begin{algorithm}
+	\label{alg:adaboost}
+	\caption{Adaboost}
+	\KwIn{Training Dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, num weak learner $N$, weak learner $L$}
+	\KwOut{Final learner $H(x)$}
+	$w_1(i) \gets \frac{1}{m}$ where i = 1, 2, ..., m \\
+	\For{$idx = 1, 2, ..., N$}
+	{
+		$h_{idx}(x) = L(D, w_{idx})$ \\
+		$\epsilon_{idx} = \Sigma_{i=1}^m w_{idx}(i) \mathbb{1}(h_{idx}(x_i) \neq y_i) $ \\
+		$\alpha_{idx} = \frac{1}{2} \log{\frac{1 - \epsilon_{idx}}{\epsilon_{idx}}}$ \\
+		$w_{idx+1}(i) = w_{idx}(i) * exp(-1 * \alpha_{idx} * y_i * h_{idx}(x_i))$ where i = 1, 2, .., m \\
+		$w_{idx+1} = \frac{w_{idx+1}}{\Sigma_{i=1}^m w_{idx}(i)}  $ \\
+	}
+	return $H(x) = \Sigma_{idx=1}^N \alpha_{idx} h_{idx}(x)$
+\end{algorithm} \par
 
-\begin{equation}
-\label{eqa: NLL}
-NLL(W) = -\Sigma_{i=1}^{m} (y_i \sigma(z) + (1 - y_i)(1 - \sigma(z)))
-\end{equation} \par
-Equation~\ref{eqa: NLL} is also called binary cross entropy.
-
-\subsection{SVM and Hinge Loss}
-Given dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, where $x_{i} \in \mathbf{R}^{n}$ and $y_{i} \in \{-1, 1\}$. SVM is based on linear regression. When given a data point, it wants: \par
-
-\begin{equation}
-\label{eqa:svm_two}
-\left\{
-\begin{array}{lr}
-w^{T}x + b \geq 1,~&if~y = 1  \\
-w^{T}x + b \leq -1,~&if~y = -1 \\
-\end{array}
-\right.
-\end{equation} \par
-Equation~\ref{eqa:svm_two} can also be written to:
-\begin{equation}
-	y(w^{T}x + b) \geq 1
-\end{equation} \par
-Other than make the classification correct, SVM also wants to make the classification boundary as safe as possible.
-To achieve that, it wants to make the margin between the positive class and negative class as large as possible.
-\par
-The positive boundary of SVM is $w^Tx + b = 1$ and negative boundary of SVM is $w^Tx + b = -1$. So the margin between this two boundary is: \par
-\begin{equation}
-	\label{eqa:margin}
-	Margin = \frac{2}{||w||}
-\end{equation} \par
-In practice, instead of maximize Equation~\ref{eqa:margin}, we want to minimize: \par
-\begin{equation}
-	\frac{w^Tw}{2}
-\end{equation} \par
-So, the optimization problem for SVM is:
-\begin{equation}
-	\begin{aligned}
-	\label{eqa:svm_optimization}
-	min_{w, b}~&\frac{w^Tw}{2} \\
-	s.t.~&y_i(w^Tx_i + b) \geq 1, i=1, 2, ..., m
-	\end{aligned}	
-\end{equation} \par
-
-Moreover, data point may not be linearly separable.
-Even the data point is linear separable, the outliers in dataset will hurt the performance of SVM.
-So, SVM introduce slack variable $\xi_i $ for each data point, which represents how much data point $i$ is on the wrong side of margin boundary.
-\par
-1. if $\xi_i = 0$, it is ok. \par
-2. if $ 0 < \xi_i < 1 $, the data point is correctly classified, but with a smaller margin than $\frac{1}{||w||}$. \par
-3. if $\xi_i > 1$, the data point is incorrectly classified. \par
-Then the optimization problem becomes: 
-\begin{equation}
-	\begin{aligned}
-	\label{eqa:svm_soft_optimization}
-	min_{w, b}~&\frac{w^Tw}{2} + \frac{C}{m}\Sigma_{i=1}^m \xi_i \\
-	s.t.~&y_i(w^Tx_i + b) \geq 1 - \xi_i, i=1, 2, ..., m
-	\end{aligned}	
-\end{equation} \par
-As $ \xi_i \geq 1 - y_i(w^Tx_i + b), i=1, 2, ..., m$, so
-\begin{equation}
-\label{eqa:xi}
-\xi_i = 
-\left\{
-\begin{array}{lr}
-	1 - y_i(w^{T}x_i + b),&if~1 - y_i(w^{T}x_i + b) \geq 0  \\
-	0,&if~1 - y_i(w^{T}x_i + b) < 0  \\
-\end{array}
-\right.
-\end{equation} \par
-So \par
-\begin{equation}
-	\label{eqa:hinge_loss}
-	\xi_i = max(0, 1 - y_i(w^Tx_i + b))
-\end{equation} \par
-Equation~\ref{eqa:hinge_loss} is the Hinge Loss (HL). Finally the optimization problem for SVM becomes
-\begin{equation}
-\label{eqa:svm_final_optimization}
-min_{w, b}~\frac{w^Tw}{2} + \frac{C}{m}\Sigma_{i=1}^m \max(0, 1 - y_i(w^Tx_i + b))
-\end{equation} \par
-We do a small modification for Equation~\ref{eqa:svm_final_optimization}, so that we can see the role of $C$ in SVM.
-\begin{equation}
-	\begin{aligned}
-	min_{w, b}~\lambda w^Tw + \frac{1}{m}\Sigma_{i=1}^m \max(0, 1 - y_i(w^Tx_i + b)) \\
-	where~\lambda = \frac{1}{2C}
-	\end{aligned}
-\end{equation} \par
-Here, we can see that $\lambda$ e.g. $\frac{1}{2C}$ is the regularizer, like Ridge Regression (RR). So, the magnitude of $W$ is in direct proportion to $C$.
+We can see that, in each iteration, the examples that correctly classified by previous weak learner, will get a smaller weight, so that current learner can pay more attention to the misclassified examples.
 
@@
 \subsection{Dataset}
-We conduct all the experiments on a9a dataset, which has total 48842 examples and each example's form is $(x, y)$, where $x \in \mathbf{R}^{123}$ and $y \in \{0, 1\}~(in~LR)~and~\{-1, +1\}~(in~SVM)$.
-We split the dataset into three part: 26049 training examples, 6512 validation examples and 16281 test examples.
-We normalized the $X_{train}, X_{val}, X_{test} $ by using the mean and variance of $X_{train}$.
+We conduct all the experiments on self constructed face/non-face dataset, which has 500 256x256 face images and 500 32x32 non-face images.
+All images have 3 channels.
+We preprocess all the images into 24x24 gray scale images.
+We then convert them by using NPD features.
+Finally, each example's form is $(x, y)$, where $x \in \mathbf{R}^{165600}$ and $y \in \{-1, +1\}$, where $+1$ means face and $-1$ means non-face.
+We randomly split the dataset into three part: 700 training examples, 100 validation examples and 200 test examples.
+$X_{train},~X_{val}~and~X_{test} $ are divided by 256 for scale purporse.
 
 \subsection{Implementation}
-We implement the LR, SVM, optimizers, initializers and loss functions using python and mainly rely on the numpy package.
+We implement the Adaboost using python and mainly rely on the numpy package.
 
-\subsection{Hyper-parameter C in SVM}
+\subsection{Weak learner's performance's effect.}
+In this section, we explore the influence of weak learner's performance in Adaboost. We set number of weak learner to five weak learner due to computation limitation. \par 
 In this section, we explore the influence of C in SVM.

### 2019-11-12 simple_ml/ensemble/model.py

@@ -72,7 +72,7 @@ class AdaBoostClassifier:
             # (2) compute error rate
             y_pred = self.classifiers[m].predict(X)
             y_pred = np.reshape(y_pred, (-1, 1))
-            error_rate = np.sum(wm * (y != y_pred)).clip(min=eps)
+            error_rate = np.sum(wm * (y != y_pred)).clip(min=eps, max=1-eps)
             # if the classifier is not good enough, we ignore it
             if error_rate > 0.5:
                 continue
@@ -101,6 +101,9 @@ class AdaBoostClassifier:
         if np.sum(self.alphas) == 0.0:
             raise ValueError('All the weak learner are ignored during training, perhaps change a weak learner.')
         for m in range(self.best_n_weakers_limit):
+            print(self.alphas[m])
+            # self.alphas[m] = 1 / self.best_n_weakers_limit
+            # print(self.alphas[m])
             ym = self.alphas[m] * self.classifiers[m].predict(X)
             ym = np.reshape(ym, (-1, 1))
             if scores is None:

### 2019-11-12 simple_ml/example/exp3/adaboost.py

@@ -1,3 +1,6 @@
+import sys
+
+sys.path.append('./')
 import os
 import random
 import pickle
@@ -11,7 +14,14 @@ from simple_ml.preprocessing import NPDFeature
 from simple_ml.ensemble import AdaBoostClassifier
 
 
-def convert_data_to_npd_feats(data_path='..\\tmp\\exp3', size=24, val_split=0.1, test_split=0.2, seed=1234):
+def accuracy(y_t, y_pred):
+    y_pred = y_pred.reshape((-1, 1))
+    return np.mean(y_t == y_pred)
+
+
+# data_path='..\\tmp\\exp3'
+def convert_data_to_npd_feats(data_path='simple_ml/example/tmp/exp3', size=24, val_split=0.1, test_split=0.2,
+                              seed=1234):
     face_img_root = os.path.join(data_path, 'face')
     non_img_root = os.path.join(data_path, 'nonface')
     faces_img_paths = os.listdir(face_img_root)
@@ -77,12 +87,14 @@ def convert_data_to_npd_feats(data_path='..\\tmp\\exp3', size=24, val_split=0.1,
 if __name__ == '__main__':
     X_train, y_train, X_val, y_val, X_test, y_test = convert_data_to_npd_feats()
     weak = DecisionTreeClassifier(max_depth=1)
-    ad = AdaBoostClassifier(weak, 20)
+    ad = AdaBoostClassifier(weak, 1)
     ad.fit(X_train, y_train, X_val, y_val, early_stop=True)
+    # ad = weak
+    ad.fit(X_train, y_train)
     y_pred = ad.predict(X_train)
     y_pred_val = ad.predict(X_val)
     y_pred_test = ad.predict(X_test)
 
-    print('Train acc: ', np.mean(y_train == y_pred))
-    print('Val acc: ', np.mean(y_val == y_pred_val))
-    print('Test acc: ', np.mean(y_test == y_pred_test))
+    print('Train acc: ', accuracy(y_train, y_pred))
+    print('Val acc: ', accuracy(y_val, y_pred_val))
+    print('Test acc: ', accuracy(y_test, y_pred_test))

### 2019-11-14 simple_ml/example/report3/paper.tex
complete report3.

@@
 \subsection{Weak learner's performance's effect.}
-In this section, we explore the influence of weak learner's performance in Adaboost. We set number of weak learner to five weak learner due to computation limitation. \par 
-In this section, we explore the influence of C in SVM.
-We set $log_{10}^{C}$ in a coarse-grained range e.g.
--2, -1, 0, 1, 2, 3, 4, and compare $loss_{val}$,  $accuracy_{val}$ and $l_2norm$ of $w$, where $loss =  \frac{w^Tw}{2} + \frac{C}{m}\Sigma_{i=1}^m \max(0, 1 - y_i(w^Tx_i + b))$ and $ l_2norm(w) = \sqrt{\Sigma_{i=1}^n w_i}$.
-We zero initilize $w$ and $b$, use SGD as optimizer with learning rate 0.001, set epoch to 200 and batch size to 64.
+In this section, we explore the influence of weak learner's performance in Adaboost. \par 
+We first explore the performance of DTC under different depths setting.
+From Fig~\ref{fig:d_weak_acc} we can see that, as the depth of DTC goes depper, its performance on training set become better but in validation set, the performance of it first gets better and then goes down which indicating the overfitting problem.
+The best performance in validation set is $89$ occurs when $depth = 4$.
 \par
-From Fig~\ref{fig:C_loss}, we can see that, when $C$ is very small, e.g.
-smaller than 1, the gradient descent process is very unstable and the loss is higher than other.
-As $C$ goes up, the loss decreases, e.g.
-from 1 to 10.
-But when $C$ gets larger than 10, the loss become slightly bigger, but still better than small $C$, like 0.01 and 0.1.
-So, we can draw the conclusion that, bigger $C$ usually better than small $C$, and the best C is in the middle, which is not very big but also not very small.
-As we can see from Fig~\ref{fig:C_loss}, $C = 10$ gets the lowest loss.
-\par
-From Fig~\ref{fig:C_acc}, we can see that, when $C$ is very small, e.g.
-0.01, the accracy in both training set and validation set is much lower than others.
-Small $C$ like 0.01 and 0.1 get worse performance comparing with others.
-In training set, the accracy is very similar when $C$ bigger than 1.
-In validation set, $C = 10$ gets slightly better performance comparing with others.
-Best validation performance under each $C$ setting can be found in Table~\ref{tab:C_performance}.
-\par
-From Fig~\ref{fig:c_mag}, we can see that, as $C$ goes up, $l_2norm(w)$ goes up except $C = 100$.
-As said above, $\frac{1}{2C}$ can be viewed as regurilizer, so when $C$ is bigger, the smaller of its impact on regurization, so the weight maginitude goes up.
+Then we explore Adaboost's performance with different weaker learner.
+We set number of weak learner to five due to computation limitation.
+We can see from Fig~\ref{fig:d_acc} that, both Adaboost and DTC suffer from overfitting prolem.
+But Adaboost outperform DTC under all setting except in validation set when depth equals to 5.
+We can see that, as the performance of weak learner goes up, the performance of Adaboost goes down, maybe due to the overfitting problem.
+The intuition is that, if a weak learner's performance is good enough in training set, then Adaboost with more weak learner is prone to overfit the dataset.
 \par
@@
 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{c_val_loss}
+		\includegraphics[width=\columnwidth]{d_weak_acc}
 		% Create a subtitle for the figure.
-		\caption{$Loss_{val}$ under different $C$.}
+		\caption{DTC accuracy under different $depth$.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:C_loss}
+		\label{fig:d_weak_acc}
 	\end{center}
@@
 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{c_val_acc}
+		\includegraphics[width=\columnwidth]{d_acc}
 		% Create a subtitle for the figure.
-		\caption{$Accuracy_{val}$ under different $C$.}
+		\caption{Adaboost and DTC accuracy under different $depth$. Note that we set number of weak learner to 5 in Adaboost.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:C_acc}
+		\label{fig:d_acc}
+	\end{center}
+\end{figure} \par
+
+\begin{table}[!hbt]
+	% Center the table
+	\begin{center}
+		% Title of the table
+		\caption{DTC and Adaboost accuracy on validation set. Best result are in bold.}
+		\label{tab:d_dtc_ad}
+		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
+		\begin{tabular}{|c|c|c|c|c|c|}
+			\hline
+			$depth$  & 1 & 2 & 3 & 4 & 5 \\
+			\hline
+			$DTC$   & 0.82 & 0.88 & 0.87 & \textbf{0.89} & 0.87   \\
+			\hline
+			$Adaboost$  & \textbf{0.96} & 0.91 & 0.94 & 0.93 & 0.85 \\
+			\hline
+		\end{tabular}
+	\end{center}
+\end{table} \par
+
+\subsection{Performance}
+Now we report the final performance of Adaboost under the best settings e.g. DTC'depth = 3 and number of weak learner = 5. The final result is shown in Fig~\ref{tab:final_performance}.
+
+\begin{table}[!hbt]
+	% Center the table
+	\begin{center}
+		% Title of the table
+		\caption{Adaboost's best accuracy. }
+		\label{tab:final_performance}
+		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
+		\begin{tabular}{|c|c|c|}
+			\hline
+			$train$  & $validation$ & $test$  \\
+			\hline
+			1.00   & 0.98 & 0.97  \\
+			\hline
+		\end{tabular}
+	\end{center}
+\end{table} \par
+
+\subsection{Number of weak learner's exploration}
+In this section, we conduct experiment on number of weak learner's exploration. \par 
+We first set the depth to 1 due to computation limitation. Under this setting, More weak Learner benefits the Adaboost, as shown in Fig~\ref{fig:n_ad_acc}.\par
+Then we evalutate the performance of Adaboost under settings that DTC' depth ranges from 1 to 5 and number of weak learner ranges from 1 to 5.
+As illustrated in Fig~\ref{fig:dn_ad_tr_acc}, in training set, Adaboost benefits from both the depth and the number of weak learners.
+Note that, as the depth of weak learner goes up, the performance gained by adaboost goes down.
+As shown in Fig~\ref{fig:dn_ad_val_acc}, when DTC's depth equals to 3, as the number of weak learner goes up, Adaboost has better performance.
+When DTC's depth equals to 5, Adaboost's performance is the worst.
+\par
+Now, we cann draw the following conclusions: \\
+1. Weaker learner gets larger performance gain in Adaboost. \\
+2. Very Strong weak learner tends to have overfitting problem in Adaboost. \\
+3. More weak learner boost the performance in Adaboost when weak learner is not very strong. \par
+
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{n_ad_acc}
+		% Create a subtitle for the figure.
+		\caption{Adaboost accuracy with different number of DTC ($depth=1$).}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:n_ad_acc}
 	\end{center}
@@
 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{c_magnitude}
+		\includegraphics[width=\columnwidth]{dn_ad_tr_acc}
 		% Create a subtitle for the figure.
-		\caption{The magnitude of $W$ under different $C$.}
+		\caption{Adaboost accuracy with different number of DTC ($depth = 1, 2, 3, 4, 5$) in training set.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:c_mag}
-	\end{center}
-\end{figure} \par
-
-\begin{table}[!hbt]
-	% Center the table
-	\begin{center}
-		% Title of the table
-		\caption{Best Result in Validation set under different C's settings. Best result are in bold.}
-		\label{tab:C_performance}
-		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
-		\begin{tabular}{|c|c|c|c|c|c|c|c|}
-			% To create a horizontal line, type \hline
-			\hline
-			% To end a column type &
-			% For a linebreak type \\
-			$log_{10}^{C}$ & -2 & -1 & 0 & 1 & 2 & 3 & 3 \\
-			\hline
-			$Accuracy_{val}$   & 84.39 & 84.42 & 84.72 & \textbf{84.75} & 84.73 & 84.56 & 84.49   \\
-			\hline
-			$Epoch$  & \textbf{2} & 86 & 62 & 138 & 173 & 147 & 145   \\
-			\hline
-		\end{tabular}
-	\end{center}
-\end{table} \par
-
-\subsection{Loss function comparision in SVM}
-In this section, we conduct experiment on loss function comparision in SVM.
-Especially, we compare two loss function, hinge loss which is illustrated above And Exponential Loss (EL), where $EL = exp\{-y_i(w^Tx_i + b)\}$.
-More formaly, $HL(z) = max(0, 1 - z)$ and $EL(z) = exp^{-z}$.
-Fig~\ref{fig:loss_fn} shows that HL and EL both have one advantage and one disadvantage.
-HL is stable when z is very mall, however EL become very large, which will lead to numeric unstable.
-EL is derivable every but HL is not derivable when $z = 1$.
-We use SGD as optimizer with learning rate 0.001, set epoch to 200, batch size to 64 and C to 10.\par
-From Fig~\ref{fig:l_val_loss} and Fig~\ref{fig:l_val_acc}, we can see that the performance of HL is superior. EL has numeric unstablity problem during gradient descent process. \par
-\begin{figure}[!hbt]
-	% Center the figure.
-	\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{loss_fn}
-		% Create a subtitle for the figure.
-		\caption{The plot of HL and EL.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:loss_fn}
+		\label{fig:dn_ad_tr_acc}
 	\end{center}
@@
 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{l_val_loss}
+		\includegraphics[width=\columnwidth]{dn_ad_val_acc}
 		% Create a subtitle for the figure.
-		\caption{$loss_{val}$ under different loss function.}
+		\caption{Adaboost accuracy with different number of DTC ($depth = 1, 2, 3, 4, 5$) in validation set.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:l_val_loss}
+		\label{fig:dn_ad_val_acc}
 	\end{center}
@@
 
-\begin{figure}[!hbt]
-	% Center the figure.
-	\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{l_val_acc}
-		% Create a subtitle for the figure.
-		\caption{$Accuracy_{val}$ under different loss function.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:l_val_acc}
-	\end{center}
-\end{figure} \par
-
-\subsection{initializer comparision in both LR and SVM}
-In this section, we compare the performance of LR and SVM under different initializers.
-We explore over ones, zeros, xavier uniform and random initializer.
-Ones initializers makes the initial $w$ to all one and Zeros initializers makes the initial $w$ to all zero.
-Xavier uniform initializer uniformally initial $w$, but bounded to interval $[-n, n]$, where $n$ is $W$'s dimension.
-Random initializer initial $w$ from standard normal distribution.
-We use SGD as optimizer with learning rate 0.001, set epoch to 200, batch size to 64 and C to 10 in SVM.
-We use HL as SVM's loss function and BCE as LR's loss function.\par
-From Fig~\ref{fig:lr_init_val_loss} and Fig~\ref{fig:lr_init_val_acc}, we can see that LR's performance is affected by the initializer.
-Typically Ones initializer brings the worst performance and Xavier uniform initializer bring the best performance.
+\section{Conclusion}
+In this report, we explore Adaboost algorithm.
+Specifically, we explore the weak learner's performance and number of weak learner in Adaboost.
+We draw the conclusions that weaker learner can get more performance gain in Adaboost and stronger learner tends to have overfitting problem in Adaboost.
+And finally we report the performance on test set under the best validation setting.
 \par
-From Fig~\ref{fig:svm_init_val_loss} and Fig~\ref{fig:svm_init_val_acc}, we can see that SVM is very robust to the initializer, different initializer doesn't disturb the performance. \par
-
-\begin{figure}[!hbt]
-	% Center the figure.
-	\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{lr_init_val_loss}
-		% Create a subtitle for the figure.
-		\caption{LR's $BCE_{val}$ under different initializer.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:lr_init_val_loss}
-	\end{center}
-\end{figure} \par
-
-\begin{figure}[!hbt]
-	% Center the figure.
-	\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{lr_init_val_acc}
-		% Create a subtitle for the figure.
-		\caption{LR's $Accuracy_{val}$ under different initializer.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:lr_init_val_acc}
-	\end{center}
-\end{figure} \par
-
-\begin{figure}[!hbt]
-	% Center the figure.
-	\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{svm_init_val_loss}
-		% Create a subtitle for the figure.
-		\caption{SVM's $HL_{val}$ under different initializer.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:svm_init_val_loss}
-	\end{center}
-\end{figure} \par
-
-\begin{figure}[!hbt]
-	% Center the figure.
-	\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{svm_init_val_acc}
-		% Create a subtitle for the figure.
-		\caption{SVM's $Accuracy_{val}$ under different initializer.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:svm_init_val_acc}
-	\end{center}
-\end{figure} \par
-
-\subsection{Optimizer comparision in both LR and SVM}
-In this section, we compare the performance of LR and SVM with different optimizers.
-We explore over Stochastic Gradient Descent (SGD), Momentum, Adam and RMSProp.
-We use xavier uniform initializer, set learning rate to 0.001 epoch to 200, batch size to 64 and C to 10 in SVM.
-We use HL as SVM's loss function and BCE as LR's loss function.\par
-From Fig~\ref{fig:lr_optim_val_loss} and Fig~\ref{fig:lr_optim_val_acc}, we can see that LR's performance is affected by the optimizer.
-Typically SGD converges very slowly; Momentum converges faster than SGD, but not as good as SGD's performance; both Adam and RMSProp converge very fast and get to the best performance.\par
-From Fig~\ref{fig:svm_optim_val_loss} and Fig~\ref{fig:svm_optim_val_acc}, we can see that SVM is very robust to the optimizer too, different optimizer didn't disturb the performance except Momentum which converges slower and get worse performance comparing with other optimizers.
-\par
-
-\begin{figure}[!hbt]
-	% Center the figure.
-	\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{lr_optim_val_loss}
-		% Create a subtitle for the figure.
-		\caption{LR's $BCE_{val}$ under different optimizer.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:lr_optim_val_loss}
-	\end{center}
-\end{figure} \par
-
-\begin{figure}[!hbt]
-	% Center the figure.
-	\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{lr_optim_val_acc}
-		% Create a subtitle for the figure.
-		\caption{LR's $Accuracy_{val}$ under different optimizer.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:lr_optim_val_acc}
-	\end{center}
-\end{figure} \par
-
-\begin{figure}[!hbt]
-	% Center the figure.
-	\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{svm_optim_val_loss}
-		% Create a subtitle for the figure.
-		\caption{SVM's $HL_{val}$ under different optimizer.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:svm_optim_val_loss}
-	\end{center}
-\end{figure} \par
-
-\begin{figure}[!hbt]
-	% Center the figure.
-	\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{svm_optim_val_acc}
-		% Create a subtitle for the figure.
-		\caption{SVM's $Accuracy_{val}$ under different optimizer.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:svm_optim_val_acc}
-	\end{center}
-\end{figure} \par
-
-\subsection{Performance on validation set and test set.}
-Now we report the final performance of LR and SVM on test set.
-For LR, we set optimizer to Adam with learning rate 0.001, batch size to 64, initializer to Xavir uniform intitializer, epoch to 200.
-For SVM, we set optimizer to Adam with learning rate 0.001, batch size to 64, initializer to Xavir uniform initializer, $C$ to 10, epoch to 200.
-\par
-Although LR is very sensitive to initializer and optimizer, but using the best initializer Xavir uniform initializer and optimizer Adam, it outperform SVM by a little under the same experiment settings and enjoys faster convergence.
-\par
-
-\begin{table}[!hbt]
-	% Center the table
-	\begin{center}
-		% Title of the table
-		\caption{Result on a9a validation set and test set. Best result are in bold.}
-		\label{tab:final_performance}
-		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
-		\begin{tabular}{|c|c|c|}
-			% To create a horizontal line, type \hline
-			\hline
-			% To end a column type &
-			% For a linebreak type \\
-			& LR & SVM \\
-			\hline
-			$Accuracy_{val}$   & \textbf{84.66} & 84.44   \\
-			\hline
-			$Accuracy_{test}$   & \textbf{84.98} & 84.88   \\
-			\hline
-			$Epoch$  & \textbf{37} & 107   \\
-			\hline
-		\end{tabular}
-	\end{center}
-\end{table} \par
-
-\section{Conclusion}
-In this report, we explore SVM and logistic regression.
-Specifically, we explore the hyper-parameter $C$ and loss function comparision in SVM, we draw the conclusion that best $C$ is something in the middle (not too small and too big) and hinge loss is better than exponential loss.
-Besides that, we also compare different initializers and optimizers in logistic regression.
-We oberseve that SVM is more robust than logistic regression under differen initializer and optimizer settings; Adam and RMSProp both obtain very good performance in logistic regression and SVM.
-Finally, we report te performance of LR and SVM under each best settings and get their performance on test set, suprisingly LR outperform SVM in a little performance.\par
 

### 2019-11-14 setup.py

@@ -1,8 +1,8 @@
 from setuptools import setup, find_packages
 
 setup(
-    name='pip_setup',
-    version='0.1.2',
+    name='simple_machine_learning',
+    version='0.1.4',
     description='simple: simple machine learning framework.',
     classifiers=[
         'License :: OSI Approved :: MIT License',

### 2019-11-14 simple_ml/__init__.py

@@ -2,3 +2,5 @@ from .utils import *
 from .preprocessing import *
 from .linear import *
 from .nn import *
+
+__name__ = 'simple_ml'

### 2019-11-14 simple_ml/ensemble/model.py

@@ -101,9 +101,6 @@ class AdaBoostClassifier:
         if np.sum(self.alphas) == 0.0:
             raise ValueError('All the weak learner are ignored during training, perhaps change a weak learner.')
         for m in range(self.best_n_weakers_limit):
-            print(self.alphas[m])
-            # self.alphas[m] = 1 / self.best_n_weakers_limit
-            # print(self.alphas[m])
             ym = self.alphas[m] * self.classifiers[m].predict(X)
             ym = np.reshape(ym, (-1, 1))
             if scores is None:

### 2019-11-14 simple_ml/example/exp3/adaboost.py

@@ -20,7 +20,8 @@ def accuracy(y_t, y_pred):
 
 
 # data_path='..\\tmp\\exp3'
-def convert_data_to_npd_feats(data_path='simple_ml/example/tmp/exp3', size=24, val_split=0.1, test_split=0.2,
+# data_path='simple_ml/example/tmp/exp3'
+def convert_data_to_npd_feats(data_path='..\\tmp\\exp3', size=24, val_split=0.1, test_split=0.2,
                               seed=1234):
     face_img_root = os.path.join(data_path, 'face')
     non_img_root = os.path.join(data_path, 'nonface')
@@ -89,7 +90,7 @@ if __name__ == '__main__':
     weak = DecisionTreeClassifier(max_depth=1)
     ad = AdaBoostClassifier(weak, 1)
     ad.fit(X_train, y_train, X_val, y_val, early_stop=True)
-    # ad = weak
+    ad = weak
     ad.fit(X_train, y_train)
     y_pred = ad.predict(X_train)
     y_pred_val = ad.predict(X_val)

### 2019-11-17 simple_ml/example/exp1/exp1.py
complete report3.

@@ -18,7 +18,7 @@ import matplotlib.pyplot as plt
 np.random.seed(1234)
 
 # read the data
-data_path = './tmp/exp1/housing.scale'
+data_path = '../tmp/exp1/housing.scale'
 X, y = load_svmlight_file(data_path)
 # convert sparse matrix to numpy array
 X = X.A
@@ -82,7 +82,7 @@ def dlr():
     model = Model(Inputs, linear_out)
     model.compile('MSE', optimizer=SGD(lr=0.01))
     model.fit(X_train, y_train,
-              verbose=-1, epochs=5000,
+              verbose=100, epochs=500,
               validation_data=(X_test, y_test),
               batch_size=256, metric='MAE',
               shuffle=True,
@@ -152,7 +152,7 @@ if __name__ == '__main__':
     # X_train = standardizer.transform(X_train)
     # X_test = standardizer.transform(X_test)
 
-    lr()
-    rlr()
-    dlr()
-    # dmlr()
+    # lr()
+    # rlr()
+    # dlr()
+    dmlr()

### 2019-11-17 simple_ml/example/exp5/embedding.py

@@ -1,0 +1,152 @@
+"""Embedding layer.
+"""
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+from .. import backend as K
+from .. import initializers
+from .. import regularizers
+from .. import constraints
+from ..engine.base_layer import Layer
+from ..legacy import interfaces
+from ..utils.generic_utils import to_list
+
+
+class Embedding(Layer):
+    """Turns positive integers (indexes) into dense vectors of fixed size.
+    eg. [[4], [20]] -> [[0.25, 0.1], [0.6, -0.2]]
+    This layer can only be used as the first layer in a model.
+    # Example
+    ```python
+      model = Sequential()
+      model.add(Embedding(1000, 64, input_length=10))
+      # the model will take as input an integer matrix of size (batch, input_length).
+      # the largest integer (i.e. word index) in the input should be
+      # no larger than 999 (vocabulary size).
+      # now model.output_shape == (None, 10, 64), where None is the batch dimension.
+      input_array = np.random.randint(1000, size=(32, 10))
+      model.compile('rmsprop', 'mse')
+      output_array = model.predict(input_array)
+      assert output_array.shape == (32, 10, 64)
+    ```
+    # Arguments
+        input_dim: int > 0. Size of the vocabulary,
+            i.e. maximum integer index + 1.
+        output_dim: int >= 0. Dimension of the dense embedding.
+        embeddings_initializer: Initializer for the `embeddings` matrix
+            (see [initializers](../initializers.md)).
+        embeddings_regularizer: Regularizer function applied to
+            the `embeddings` matrix
+            (see [regularizer](../regularizers.md)).
+        activity_regularizer: Regularizer function applied to
+            the output of the layer (its "activation").
+            (see [regularizer](../regularizers.md)).
+        embeddings_constraint: Constraint function applied to
+            the `embeddings` matrix
+            (see [constraints](../constraints.md)).
+        mask_zero: Whether or not the input value 0 is a special "padding"
+            value that should be masked out.
+            This is useful when using [recurrent layers](recurrent.md)
+            which may take variable length input.
+            If this is `True` then all subsequent layers
+            in the model need to support masking or an exception will be raised.
+            If mask_zero is set to True, as a consequence, index 0 cannot be
+            used in the vocabulary (input_dim should equal size of
+            vocabulary + 1).
+        input_length: Length of input sequences, when it is constant.
[…]

### 2019-11-17 simple_ml/example/exp5/target.py

@@ -1,0 +1,260 @@
+import sys
+import numpy
+from pandas import read_csv
+from keras.layers import Input, Embedding, Dot, Add, Flatten, Lambda, Dense
+from keras.models import Model
+from keras.initializers import RandomNormal
+from keras.regularizers import l2
+from keras.callbacks import EarlyStopping
+from keras import backend as K
+
+from keras.layers import Dot
+
+class MatrixFactorization:
+    def __init__(self, userCount, itemCount, embeddingDimension=10, regularizationScale=0.0, epochCount=20,
+                 validationRatio=0.1, batchSize=256, openBias=False, openLambdaLayer=True):
+        self.userCount = userCount
+        self.itemCount = itemCount
+        self.embeddingDimension = embeddingDimension
+        self.regularizationScale = regularizationScale
+        self.epochCount = epochCount
+        self.validationRatio = validationRatio
+        self.batchSize = batchSize
+        self.openBias = openBias
+        self.openLambdaLayer = openLambdaLayer
+
+        self.build()
+
+    def build(self):
+        # Define user input -- user index (an integer)
+        self.userInputLayer = Input(shape=(1,), dtype="int32")
+
+        # Define item input -- item index (an integer)
+        self.itemInputLayer = Input(shape=(1,), dtype="int32")
+
+        # Define user embedding matrix
+        # Embedding oject returns a neural layer as function y = f(x) 
+        #     then we assign its input x = userInputLayer and output y = userEmbeddingLayer, that is,
+        #     f = Embedding( ... ) 
+        #     userEmbeddingLayer = f(userInputLayer)
+        # Argument input_length corresponds to the dimension of input layer -- user index, a single integer
+        # We adopt additional Flatten() layer to transform the default output tensor shape (batch_size, input_length = 1, input_dim)
+        #     to shape (batch_size, input_dim), that is, eliminate the extra dimension of Embedding outputs
+        # batch_size is actually the size of a mini-batch
+        self.userEmbeddingLayer = Embedding(input_dim=self.userCount, output_dim=self.embeddingDimension,
+                                            input_length=1,
+                                            embeddings_regularizer=l2(self.regularizationScale),
+                                            embeddings_initializer=RandomNormal())(self.userInputLayer)
[…]

### 2019-11-17 simple_ml/nn/layer.py

@@ -156,7 +156,7 @@ class Input(Layer):
         raise ValueError('Input layer is not callable.')
 
     def forward(self, inputs, *args, **kwargs):
-        inputs = np.asarray(inputs)
+        inputs = np.asarray(inputs, dtype=self.dtype)
         assert self.input_shape[1:] == inputs.shape[1:]
         self.input_shape = inputs.shape
         self.output_shape = self.input_shape
@@ -739,3 +739,198 @@ class AvgPool2D(Layer):
 # alias names
 MaxPooling2D = MaxPool2D
 AvgPooling2D = AvgPool2D
+
+
+class Embedding(Layer):
+    def __init__(self,
+                 input_dim,
+                 output_dim,
+                 regularizer=None,
+                 initializer=xavier_uniform_initializer):
+        super(Embedding, self).__init__()
+        pass
+        self.input_dim = input_dim
+        self.output_dim = output_dim
+        self.regularizer = get_regularizer(regularizer)
+        self.initializer = get_initializer(initializer)
+        self.input_shape = None
+        self.output_shape = None
+        if self.input_dim is not None:
+            self.connection(None)
+
+    def connection(self, pre_layer):
+        self.pre_layer = pre_layer
+        if pre_layer is None:
+            if self.input_dim is None:
+                raise ValueError('input_size must not be `None` as the first layer.')
+            self.input_shape = [None, self.input_dim]
+            self.output_shape = [None, self.output_dim]
+        else:
+            pre_layer.next_layer = self
+            self.input_dim = pre_layer.output_shape[1]
+            self.input_shape = pre_layer.output_shape
+            self.output_shape = [self.input_shape[0], self.output_dim]
+        self.weight = self.initializer([self.output_dim, self.input_dim])
+        self.bias = self.initializer([self.output_dim])
+        self.delta_weight = np.zeros([self.output_dim, self.input_dim])
+        self.delta_bias = np.zeros([self.output_dim])
+        self.delta = np.zeros([self.input_dim])
+
+
+class _Merge(Layer):
+    """Generic merge layer for elementwise merge functions.
+
+    Used to implement `Sum`, `Average`, etc.
+
+    """
+
+    def __init__(self):
+        super(_Merge, self).__init__()
+
+    def _merge_function(self, inputs):
+        raise NotImplementedError
+
+    def _compute_elemwise_op_output_shape(self, shape1, shape2):
+        """Computes the shape of the resultant of an elementwise operation.
+
+        # Arguments
[…]

### 2019-11-17 simple_ml/nn/model.py

@@ -445,11 +445,25 @@ class Model(Module):
         self.output = output
 
     def forward(self, X, is_training=False, *args, **kwargs):
+        """
+
+        ideal forward pass:
+        build hash table (implement with python dict)
+        {
+            node: next_list;
+            '1': [2, 3, 4],
+            '2': [3],
+            '3': [4]
+        }
+        """
         layer = self.input
         while layer is not None:
             X = layer.forward(X, is_training=is_training)
             layer = layer.next_layer
         return X
+
+
+
 
     def regularizer_loss(self):
         reg_loss = 0

### 2019-11-17 simple_ml/nn/layer.py
add factorization.

@@ -741,196 +741,121 @@ MaxPooling2D = MaxPool2D
 AvgPooling2D = AvgPool2D
 
 
-class Embedding(Layer):
-    def __init__(self,
-                 input_dim,
-                 output_dim,
+class Factorization(Layer):
+    def __init__(self, a_dim, b_dim, k,
+                 activation=None,
                  regularizer=None,
                  initializer=xavier_uniform_initializer):
-        super(Embedding, self).__init__()
-        pass
-        self.input_dim = input_dim
-        self.output_dim = output_dim
+        super(Factorization, self).__init__()
+        self.input_dim = (1, 1)
+        self.a_dim = a_dim
+        self.b_dim = b_dim
+        self.k = k
+        self.output_dim = 1
         self.regularizer = get_regularizer(regularizer)
+        self.activation = get_activation(activation)
         self.initializer = get_initializer(initializer)
         self.input_shape = None
         self.output_shape = None
         if self.input_dim is not None:
             self.connection(None)
 
+    @property
+    def embedding_a(self):
+        return self.__embedding_a
+
+    @property
+    def embedding_b(self):
+        return self.__embedding_b
+
+    @property
+    def delta_embedding_a(self):
+        return self.__delta_embedding_a
+
+    @property
+    def delta_embedding_b(self):
+        return self.__delta_embedding_b
+
+    @embedding_a.setter
+    def embedding_a(self, embedding_a):
+        self.__embedding_a = embedding_a
+
+    @embedding_b.setter
+    def embedding_b(self, embedding_b):
+        self.__embedding_b = embedding_b
+
+    @delta_embedding_a.setter
+    def delta_embedding_a(self, delta_embedding_a):
+        self.__delta_embedding_a = delta_embedding_a
+
+    @delta_embedding_b.setter
+    def delta_embedding_b(self, delta_embedding_b):
+        self.__delta_embedding_b = delta_embedding_b
+
+    @property
+    def params(self):
+        return [self.embedding_a, self.embedding_b]
+
+    @property
+    def grads(self):
+        return [self.delta_embedding_a, self.delta_embedding_b]
+
+    def call(self, pre_layer=None, *args, **kwargs):
+        self.connection(pre_layer)
+        return self
+
     def connection(self, pre_layer):
         self.pre_layer = pre_layer
         if pre_layer is None:
             if self.input_dim is None:
                 raise ValueError('input_size must not be `None` as the first layer.')
[…]

### 2019-11-18 simple_ml/example/exp5/embedding.py
complete factorization and start exp5.

@@ -1,152 +1,0 @@
-"""Embedding layer.
-"""
-from __future__ import absolute_import
-from __future__ import division
-from __future__ import print_function
-
-from .. import backend as K
-from .. import initializers
-from .. import regularizers
-from .. import constraints
-from ..engine.base_layer import Layer
-from ..legacy import interfaces
-from ..utils.generic_utils import to_list
-
-
-class Embedding(Layer):
-    """Turns positive integers (indexes) into dense vectors of fixed size.
-    eg. [[4], [20]] -> [[0.25, 0.1], [0.6, -0.2]]
-    This layer can only be used as the first layer in a model.
-    # Example
-    ```python
-      model = Sequential()
-      model.add(Embedding(1000, 64, input_length=10))
-      # the model will take as input an integer matrix of size (batch, input_length).
-      # the largest integer (i.e. word index) in the input should be
-      # no larger than 999 (vocabulary size).
-      # now model.output_shape == (None, 10, 64), where None is the batch dimension.
-      input_array = np.random.randint(1000, size=(32, 10))
-      model.compile('rmsprop', 'mse')
-      output_array = model.predict(input_array)
-      assert output_array.shape == (32, 10, 64)
-    ```
-    # Arguments
-        input_dim: int > 0. Size of the vocabulary,
-            i.e. maximum integer index + 1.
-        output_dim: int >= 0. Dimension of the dense embedding.
-        embeddings_initializer: Initializer for the `embeddings` matrix
-            (see [initializers](../initializers.md)).
-        embeddings_regularizer: Regularizer function applied to
-            the `embeddings` matrix
-            (see [regularizer](../regularizers.md)).
-        activity_regularizer: Regularizer function applied to
-            the output of the layer (its "activation").
-            (see [regularizer](../regularizers.md)).
-        embeddings_constraint: Constraint function applied to
-            the `embeddings` matrix
-            (see [constraints](../constraints.md)).
-        mask_zero: Whether or not the input value 0 is a special "padding"
-            value that should be masked out.
-            This is useful when using [recurrent layers](recurrent.md)
-            which may take variable length input.
-            If this is `True` then all subsequent layers
-            in the model need to support masking or an exception will be raised.
-            If mask_zero is set to True, as a consequence, index 0 cannot be
-            used in the vocabulary (input_dim should equal size of
-            vocabulary + 1).
-        input_length: Length of input sequences, when it is constant.
[…]

### 2019-11-18 simple_ml/example/exp5/exp5.py

@@ -1,0 +1,104 @@
+import numpy as np
+
+from sklearn.datasets import load_svmlight_file
+from sklearn.model_selection import train_test_split
+
+from simple_ml.utils.distance import euclidean
+from simple_ml.preprocessing.general import Standardizer
+from simple_ml.linear.model import LinearRegression, RidgeRegression
+from simple_ml.nn.layer import Factorization, Input
+from simple_ml.nn.model import Model
+from simple_ml.nn.initializer import zeros, ones
+from simple_ml.nn.regularizer import L2_Regularizer, L1_Regularizer
+from simple_ml.nn.optimizer import SGD, Momentum, Adam, RMSProp
+from simple_ml.utils.metric import accuracy, absolute_error, square_error
+
+import matplotlib.pyplot as plt
+
+# fix random seed
+np.random.seed(1234)
+
+
+def read_data(data_path='../tmp/exp5/ml-100k/u.data', val_split=0.1, test_split=0.2):
+    # read the data
+    triples = []
+    with open(data_path) as f:
+        for line in f.readlines():
+            triples.append([int(i) for i in line.split('\t')[:-1]])
+    Data = np.array(triples, dtype=np.int)
+    total_size = Data.shape[0]
+    train_size = int(total_size - (val_split + test_split) * total_size)
+    val_size = int(train_size + val_split * total_size)
+    Data_train = Data[:train_size]
+    Data_val = Data[train_size:val_size]
+    Data_test = Data[val_size:]
+
+    def data_to_Xy(data):
+        # start from index 0
+        return data[:, :-1] - 1, np.reshape(data[:, -1], (-1, 1))
+
+    X_train, y_train = data_to_Xy(Data_train)
+    X_val, y_val = data_to_Xy(Data_val)
+    X_test, y_test = data_to_Xy(Data_test)
+
+    num_user = len(np.unique(Data[:, 0]))
+    num_item = len(np.unique(Data[:, 1]))
+    print('Number of unique user: %d' % num_user)
+    print('Number of unique item: %d' % num_item)
+    print('X_train: ', X_train.shape, ' y_train: ', y_train.shape)
+    print('X_val: ', X_val.shape, ' y_val: ', y_val.shape)
+    print('X_test: ', X_test.shape, ' y_test: ', y_train.shape)
+    print()
+    return X_train, y_train, X_val, y_val, X_test, y_test, num_user, num_item
+
+
+def dlr():
[…]

### 2019-11-18 simple_ml/example/exp5/target.py

@@ -1,260 +1,0 @@
-import sys
-import numpy
-from pandas import read_csv
-from keras.layers import Input, Embedding, Dot, Add, Flatten, Lambda, Dense
-from keras.models import Model
-from keras.initializers import RandomNormal
-from keras.regularizers import l2
-from keras.callbacks import EarlyStopping
-from keras import backend as K
-
-from keras.layers import Dot
-
-class MatrixFactorization:
-    def __init__(self, userCount, itemCount, embeddingDimension=10, regularizationScale=0.0, epochCount=20,
-                 validationRatio=0.1, batchSize=256, openBias=False, openLambdaLayer=True):
-        self.userCount = userCount
-        self.itemCount = itemCount
-        self.embeddingDimension = embeddingDimension
-        self.regularizationScale = regularizationScale
-        self.epochCount = epochCount
-        self.validationRatio = validationRatio
-        self.batchSize = batchSize
-        self.openBias = openBias
-        self.openLambdaLayer = openLambdaLayer
-
-        self.build()
-
-    def build(self):
-        # Define user input -- user index (an integer)
-        self.userInputLayer = Input(shape=(1,), dtype="int32")
-
-        # Define item input -- item index (an integer)
-        self.itemInputLayer = Input(shape=(1,), dtype="int32")
-
-        # Define user embedding matrix
-        # Embedding oject returns a neural layer as function y = f(x) 
-        #     then we assign its input x = userInputLayer and output y = userEmbeddingLayer, that is,
-        #     f = Embedding( ... ) 
-        #     userEmbeddingLayer = f(userInputLayer)
-        # Argument input_length corresponds to the dimension of input layer -- user index, a single integer
-        # We adopt additional Flatten() layer to transform the default output tensor shape (batch_size, input_length = 1, input_dim)
-        #     to shape (batch_size, input_dim), that is, eliminate the extra dimension of Embedding outputs
-        # batch_size is actually the size of a mini-batch
-        self.userEmbeddingLayer = Embedding(input_dim=self.userCount, output_dim=self.embeddingDimension,
-                                            input_length=1,
-                                            embeddings_regularizer=l2(self.regularizationScale),
-                                            embeddings_initializer=RandomNormal())(self.userInputLayer)
[…]

### 2019-11-18 simple_ml/nn/layer.py

@@ -13,6 +13,7 @@ __all__ = [
     'Conv2d',
     'AvgPooling2D', 'AvgPool2D',
     'MaxPooling2D', 'MaxPool2D',
+    'Factorization',
 ]
 
 
@@ -743,6 +744,7 @@ AvgPooling2D = AvgPool2D
 
 class Factorization(Layer):
     def __init__(self, a_dim, b_dim, k,
+                 use_bias=True,
                  activation=None,
                  regularizer=None,
                  initializer=xavier_uniform_initializer):
@@ -751,6 +753,7 @@ class Factorization(Layer):
         self.a_dim = a_dim
         self.b_dim = b_dim
         self.k = k
+        self.use_bias = use_bias
         self.output_dim = 1
         self.regularizer = get_regularizer(regularizer)
         self.activation = get_activation(activation)
@@ -769,12 +772,28 @@ class Factorization(Layer):
         return self.__embedding_b
 
     @property
+    def bias_a(self):
+        return self.__bias_a
+
+    @property
+    def bias_b(self):
+        return self.__bias_b
+
+    @property
     def delta_embedding_a(self):
         return self.__delta_embedding_a
 
     @property
     def delta_embedding_b(self):
         return self.__delta_embedding_b
+
+    @property
+    def delta_bias_a(self):
+        return self.__delta_bias_a
+
+    @property
+    def delta_bias_b(self):
+        return self.__delta_bias_b
 
     @embedding_a.setter
     def embedding_a(self, embedding_a):
@@ -784,6 +803,14 @@ class Factorization(Layer):
     def embedding_b(self, embedding_b):
         self.__embedding_b = embedding_b
 
+    @bias_a.setter
+    def bias_a(self, bias_a):
+        self.__bias_a = bias_a
+
+    @bias_b.setter
+    def bias_b(self, bias_b):
+        self.__bias_b = bias_b
+
     @delta_embedding_a.setter
     def delta_embedding_a(self, delta_embedding_a):
         self.__delta_embedding_a = delta_embedding_a
@@ -792,13 +819,27 @@ class Factorization(Layer):
     def delta_embedding_b(self, delta_embedding_b):
         self.__delta_embedding_b = delta_embedding_b
 
+    @delta_bias_a.setter
+    def delta_bias_a(self, delta_bias_a):
+        self.__delta_bias_a = delta_bias_a
+
+    @delta_bias_b.setter
+    def delta_bias_b(self, delta_bias_b):
+        self.__delta_bias_b = delta_bias_b
+
     @property
[…]

### 2019-11-18 simple_ml/nn/model.py

@@ -62,11 +62,14 @@ class Module(object):
             return []
         return self.valid_metrics[self.metric]
 
-    def best_performance(self):
+    def best_performance(self, bigger=True):
         performance = {}
         key = 'train_set'
         tr_metrics = np.array(self.training_metrics[self.metric])
-        best_epoch = tr_metrics.argmax()
+        if bigger:
+            best_epoch = tr_metrics.argmax()
+        else:
+            best_epoch = tr_metrics.argmin()
         best_metric = tr_metrics[best_epoch]
         best_loss = self.training_losses[best_epoch]
         performance[key] = {
@@ -85,7 +88,10 @@ class Module(object):
 
         else:
             val_metrics = np.array(self.valid_metrics[self.metric])
-            best_epoch = val_metrics.argmax()
+            if bigger:
+                best_epoch = val_metrics.argmax()
+            else:
+                best_epoch = val_metrics.argmin()
             best_metric = val_metrics[best_epoch]
             best_loss = self.valid_losses[best_epoch]
             performance[key] = {
@@ -252,7 +258,9 @@ class Module(object):
                     description = 'Epoch: {} | Loss: {:.4f} | Metric: {:.4f}'.format(iter_idx, per_loss, per_metric)
                 # tqdm_gen.set_description(description)
 
-            train_losses = train_losses / train_size + self.regularizer_loss()
+            # Don't reg loss get better vision
+            # train_losses = train_losses / train_size + self.regularizer_loss()
+            train_losses = train_losses / train_size
             train_matrices = train_matrices / train_size
 
             run_out = "epoch %5d/%5d, train-[loss: %.4f" % (
@@ -282,7 +290,9 @@ class Module(object):
                     if metric is not None:
                         valid_matrices += metric(y_pred, y_batch)
 
-                valid_losses = valid_losses / val_size + self.regularizer_loss()
+                # Don't reg loss get better vision
+                # valid_losses = valid_losses / val_size + self.regularizer_loss()
+                valid_losses = valid_losses / val_size
                 valid_matrices = valid_matrices / val_size
 
                 run_out += "valid-[loss: %.4f" % (float(valid_losses))
@@ -461,9 +471,6 @@ class Model(Module):
             X = layer.forward(X, is_training=is_training)
             layer = layer.next_layer
         return X
-
-
-
 
     def regularizer_loss(self):
         reg_loss = 0

### 2019-11-18 simple_ml/example/report5/paper.tex
complete report5..

--- 2019-11-14 simple_ml/example/report3/paper.tex
@@
 % Define document title and author
-	\title{Adaboost for face image classification}
+	\title{Recommender System Based on Matrix Factorization}
 	\maketitle
@@
 \begin{abstract}
-In this report, we solve the face/non-face classification problem by adaboost with Decision Tree Classifier (DTC) as weak learner. \\
+In this report, we solve the Recommendation System problem based on Matrix Factorization (MF). \\
 We perform experiments on three aspects: \\
-1. Weak learner's performance effect. \\
-2. Number of weak learner's exploration. \\
+1. Hidden dimension's impact. \\
+2. Loss function's impact. \\
+3. Regularizer's impact. \\
 \end{abstract}
@@
 	% \PARstart{}{} creates a tall first letter for this first paragraph
-\PARstart{A}{daboost} short for "Adaptive Boosting",  is an ensemble method that combine a bunch of weak learners into a strong learner which outperforms all the weak learners.
-It's wildly used in academic and industry community, which make it very important for us to fully explore it.
-We will explore the the effect of weak learner's performance and the performance with different number of weak learner.
+\PARstart{M}{atrix} Factorization is a class of collaborative filtering algorithms used in recommender systems.
+Matrix factorization algorithms work by decomposing the user-item interaction matrix into the product of two lower dimensionality rectangular matrices Usually, the user-item interaction matrix is very sparse e.g.
+a lot of zeros or mising values in it.
+The adavantage of MF is that it transforms a sparse matrix into two lower dimensionality matrices which are regarded as User Embeddings (UE) and Item Embeddings (IE) respectively.
+MF is wildly used in academic and industry community, which make it very important for us to fully explore it.
+We will explore it under different settings.
 
@@
 \section{Methods and Theory}
-In this part, we define Adaboost algorithm.
-\subsection{Adaboost}
-Given dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, where $x_{i} \in \mathbf{R}^{n}$.
-$y_{i} \in \{-1, 1\}$ and weak Learner $L(x) \in \{-1, 1\} $, Adaboost algorithm can be found in Algorithm~\ref{alg:adaboost}.
-\par
-
-\begin{algorithm}
-	\label{alg:adaboost}
-	\caption{Adaboost}
-	\KwIn{Training Dataset $ D=\{x_{i}, y_{i}\}_{i=1}^{m}$, num weak learner $N$, weak learner $L$}
-	\KwOut{Final learner $H(x)$}
-	$w_1(i) \gets \frac{1}{m}$ where i = 1, 2, ..., m \\
-	\For{$idx = 1, 2, ..., N$}
-	{
-		$h_{idx}(x) = L(D, w_{idx})$ \\
-		$\epsilon_{idx} = \Sigma_{i=1}^m w_{idx}(i) \mathbb{1}(h_{idx}(x_i) \neq y_i) $ \\
-		$\alpha_{idx} = \frac{1}{2} \log{\frac{1 - \epsilon_{idx}}{\epsilon_{idx}}}$ \\
-		$w_{idx+1}(i) = w_{idx}(i) * exp(-1 * \alpha_{idx} * y_i * h_{idx}(x_i))$ where i = 1, 2, .., m \\
-		$w_{idx+1} = \frac{w_{idx+1}}{\Sigma_{i=1}^m w_{idx}(i)}  $ \\
-	}
-	return $H(x) = \Sigma_{idx=1}^N \alpha_{idx} h_{idx}(x)$
-\end{algorithm} \par
-
-We can see that, in each iteration, the examples that correctly classified by previous weak learner, will get a smaller weight, so that current learner can pay more attention to the misclassified examples.
+In this part, we define Matrix Factorization algorithm.
+\subsection{Matrix Factorization}
+Given a rating matrix $\mathbf{R} \in \mathbb{R}^{m \times n} $, with sparse ratings from m users to n items.
+MF factorizes $\mathbf{R}$ into $P$ and $Q$, where $P \in \mathbb{R}^{m \times h }$, $Q \in \mathbb{R}^{n \times h}$ and $h$ is the hidden dimension which is a hyper-parameter.
+In this way, rating matrix can be expressed as $\mathbf{R} = P Q^{T}$.
+Usually, $h \ll min(m, n)$.
+The Space complexity is $O(m*n)$ for $\mathbf{R}$ and $O((m+n)*h)$ for $P$ and $Q$, where $O((m+n)*h) \ll O(m*n)$.
+So MF can be used for space saving strategy in some scenarios.
+Beyond that, the factorized $P$ and $Q$ can be used for unseen user-item pair prediction, which is the core of MF.\par
 
@@
 \subsection{Dataset}
-We conduct all the experiments on self constructed face/non-face dataset, which has 500 256x256 face images and 500 32x32 non-face images.
-All images have 3 channels.
-We preprocess all the images into 24x24 gray scale images.
-We then convert them by using NPD features.
-Finally, each example's form is $(x, y)$, where $x \in \mathbf{R}^{165600}$ and $y \in \{-1, +1\}$, where $+1$ means face and $-1$ means non-face.
-We randomly split the dataset into three part: 700 training examples, 100 validation examples and 200 test examples.
-$X_{train},~X_{val}~and~X_{test} $ are divided by 256 for scale purporse.
+We conduct all the experiments on MovieLens-100k dataset, which contains 10,000 comments from 943 users out of 1682 movies.
+Each comment's form is $(user_{id}, item_{id}, rating)$, where $ rating \in \{1, 2, 3, 4, 5\}$.
+We randomly split the dataset into three part: 70,000 training examples, 10,000 validation examples and 20,000 test examples.
+\par
 
 \subsection{Implementation}
-We implement the Adaboost using python and mainly rely on the numpy package.
+We implement the Matrix Factorization using python and mainly rely on the numpy package.
+The initializer for $P$ and $Q$ is Xavier uniform initializer, which initial matrix $M$, but bounded to interval $[-a*b, a*b]$, where $n$ is $M \in \mathbb{R}^{a\times b}$.
+We use Adam optimizer with leraning rate 0.001, set batch size to 256 and epoch to 200.
+We use $MAE$ as evalutation metric.
+If not sepecifficly stated, we use $h = 10$, $MSE$ as loss function and $l_2~Regularizer$ as regularizer and penalty cofficient 0.1 in regularizer.
 
-\subsection{Weak learner's performance's effect.}
-In this section, we explore the influence of weak learner's performance in Adaboost. \par 
-We first explore the performance of DTC under different depths setting.
-From Fig~\ref{fig:d_weak_acc} we can see that, as the depth of DTC goes depper, its performance on training set become better but in validation set, the performance of it first gets better and then goes down which indicating the overfitting problem.
-The best performance in validation set is $89$ occurs when $depth = 4$.
+\subsection{Hidden dimension's impact}
+In this section, we explore the influence of hidden dimension in MF. We validate the hidden dimension in MF in a range, e.g. 1, 5, 10, 15, 20, 25, 30. \par 
+From Fig~\ref{fig:h_mae} we can see that, bigger $h$ tends to have overfitting problem.
+As presented in Table~\ref{tab:h_mae}, $d = 10$ gets the best performance in validation set.
+Surprisingly, $h=1$ still get $MAE$ about $0.7522$ in validation set, which is not very far from the best performance e.g.
+$0.7259$, but $h=1$ can be very time-efficiency and space-saving.
 \par
-Then we explore Adaboost's performance with different weaker learner.
-We set number of weak learner to five due to computation limitation.
-We can see from Fig~\ref{fig:d_acc} that, both Adaboost and DTC suffer from overfitting prolem.
-But Adaboost outperform DTC under all setting except in validation set when depth equals to 5.
-We can see that, as the performance of weak learner goes up, the performance of Adaboost goes down, maybe due to the overfitting problem.
-The intuition is that, if a weak learner's performance is good enough in training set, then Adaboost with more weak learner is prone to overfit the dataset.
-\par
+From Fig~\ref{fig:h_tr_losses} and Fig~\ref{fig:h_val_losses} we can see that, bigger $h$ converges faster. \par
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{h_mae}
+		% Create a subtitle for the figure.
+		\caption{MF $MAE$ under different $h$.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:h_mae}
+	\end{center}
+\end{figure} \par
+
+\begin{table}[!hbt]
+	% Center the table
+	\begin{center}
+		% Title of the table
+		\caption{MTC $MAE$ under different $h$. Best result are in bold.}
+		\label{tab:h_mae}
+		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
+		\begin{tabular}{|c|c|c|c|c|c|c|c|}
+			\hline
+			$h$  & 1 & 5 & 10 & 15 & 20 & 25 & 30 \\
+			\hline
+			$MAE_{train}$ & 0.7211 & 0.6216 & 0.5758 & 0.5478 & 0.5302 & 0.5191 & \textbf{0.5124}  \\
+			\hline
+			$MAE_{val}$  & 0.7522 & 0.7276 & \textbf{0.7259} & 0.7262 & 0.7265 &  0.7321 & 0.7349  \\
+			\hline
+		\end{tabular}
+	\end{center}
+\end{table} \par
 
@@
 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{d_weak_acc}
+		\includegraphics[width=\columnwidth]{h_tr_losses}
 		% Create a subtitle for the figure.
-		\caption{DTC accuracy under different $depth$.}
+		\caption{MF $MSE_{train}$ under different $d$ and $epoch$. }
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:d_weak_acc}
+		\label{fig:h_tr_losses}
 	\end{center}
@@
 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{d_acc}
+		\includegraphics[width=\columnwidth]{h_val_losses}
 		% Create a subtitle for the figure.
-		\caption{Adaboost and DTC accuracy under different $depth$. Note that we set number of weak learner to 5 in Adaboost.}
+		\caption{MF $MSE_{val}$ under different $d$ and $epoch$. }
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:d_acc}
+		\label{fig:h_val_losses}
+	\end{center}
+\end{figure} \par
+
+\subsection{Loss function's impact}
+In this section, we explore the impact of loss function in MF. In particular, we evaluate three loss functions: \\ \\
+1. $MAE(y, \hat{y}) = \frac{1}{m}\Sigma_{i=1}^{m}|y_i - \hat{y_i}|$ \\ \\
+2. $MSE(y, \hat{y}) = \frac{1}{2m}\Sigma_{i=1}^{m}(y_i - \hat{y_i})^2$ \\ \\
+3. $HB(y, \hat{y}) = \frac{1}{m}\Sigma_{i=1}^{m}L_{\delta }(y_i, \hat{y_i}) $ \\ \\
+where, $ L_{\delta }(y_i,\hat{y_i})={\begin{cases}{\frac  {1}{2}}(y_i-\hat{y_i})^{2}&{\textrm  {for}}~|y_i-\hat{y_i}|\leq \delta ,\\\delta \,|y_i-\hat{y_i}|-{\frac  {1}{2}}\delta ^{2}&{\textrm  {otherwise.}}\end{cases}}$ \\ \\
+We set $\delta = 1$. \par
+Three loss functions are mean absolute error, mean squared error and huber loss respectively.
+The plot of $MAE(x)$, $MSE(s)$ and $HB(x)$ can be found in Fig~\ref{fig:loss_fns}.
+Huber Loss can been viewed as a combination of $MSE$ and $MAE$.
+\par
+From Fig~\ref{fig:loss_val_mae}, we can see that, HB gets the best performance on validation set.
+Intuitively, HB takes MAE's adavantage that robust to outliers and MSE's adavantage that smooth in low error region, so it's prone to perform well.
+The detailed result can be found in Table~\ref{tab:loss_mae}.
+\par
+
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{loss_fns}
+		% Create a subtitle for the figure.
+		\caption{$MAE$, $MSE$ and $HB$ plot.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:loss_fns}
 	\end{center}
@@
 		% Title of the table
-		\caption{DTC and Adaboost accuracy on validation set. Best result are in bold.}
-		\label{tab:d_dtc_ad}
+		\caption{MF's performance under different loss function settings. Best result are in bold.}
+		\label{tab:loss_mae}
 		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
-		\begin{tabular}{|c|c|c|c|c|c|}
+		\begin{tabular}{|c|c|c|c|}
 			\hline
-			$depth$  & 1 & 2 & 3 & 4 & 5 \\
+			$loss_{fn}$  & $MAE$ & $MSE$ & $HB$  \\
 			\hline
-			$DTC$   & 0.82 & 0.88 & 0.87 & \textbf{0.89} & 0.87   \\
-			\hline
-			$Adaboost$  & \textbf{0.96} & 0.91 & 0.94 & 0.93 & 0.85 \\
+			$MAE_{val}$ & 0.7293 & 0.7244 & \textbf{0.7217} \\
 			\hline
@@
 
-\subsection{Performance}
-Now we report the final performance of Adaboost under the best settings e.g. DTC'depth = 3 and number of weak learner = 5. The final result is shown in Fig~\ref{tab:final_performance}.
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{loss_val_mae}
+		% Create a subtitle for the figure.
+		\caption{MF $MAE_{val}$ under different loss functions.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:loss_val_mae}
+	\end{center}
+\end{figure} \par
+
+\subsection{Regularizer's impact}
+In this section, we explore the impact of regularizer in MF. In particular, we evaluate three regularizers: \\ \\
+1. $L1(w) = \lambda * \Sigma_{i} |w_i| $ \\ \\
+2. $L2(w) = \lambda * \Sigma_{i} w_i^2 $ \\ \\
+3. $L1\_L2(w) = \frac{L1(w) + L2(w)}{2}  $ \\ \\
+We set $\lambda = 0.01$ in all experiments. \par
+$L1\_L2$ regularizer can be seen as a combination of $L1$ and $L2$ regularizer. The plot of three regularizers can be found in Fig~\ref{fig:regs}.\par
+From Fig~\ref{fig:reg_val_mae}, we can see that, $L2$ gets the best performance on validation set.
+$L1\_L2$ has sever overffiting problem than $L1$ and $L2$ after many epoches.
+However, $L1\_L2$ gets better performance than $L1$.
+\par
+
+\begin{figure}[!hbt]
+	% Center the figure.
+	\begin{center}
+		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
+		\includegraphics[width=\columnwidth]{regs}
+		% Create a subtitle for the figure.
+		\caption{$L1$, $L2$ and $L1\_L2$ plot.}
+		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
+		\label{fig:regs}
+	\end{center}
+\end{figure} \par
 
@@
 		% Title of the table
-		\caption{Adaboost's best accuracy. }
-		\label{tab:final_performance}
+		\caption{MF's performance under different regularizer settings. Best result are in bold.}
+		\label{tab:reg_mae}
 		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
-		\begin{tabular}{|c|c|c|}
+		\begin{tabular}{|c|c|c|c|}
 			\hline
-			$train$  & $validation$ & $test$  \\
+			$Regularizer$  & $L1$ & $L2$ & $L1\_L2$  \\
 			\hline
-			1.00   & 0.98 & 0.97  \\
+			$MAE_{val}$ & 0.7537 & \textbf{0.7243} & 0.7358 \\
 			\hline
@@
 
-\subsection{Number of weak learner's exploration}
-In this section, we conduct experiment on number of weak learner's exploration. \par 
-We first set the depth to 1 due to computation limitation. Under this setting, More weak Learner benefits the Adaboost, as shown in Fig~\ref{fig:n_ad_acc}.\par
-Then we evalutate the performance of Adaboost under settings that DTC' depth ranges from 1 to 5 and number of weak learner ranges from 1 to 5.
-As illustrated in Fig~\ref{fig:dn_ad_tr_acc}, in training set, Adaboost benefits from both the depth and the number of weak learners.
-Note that, as the depth of weak learner goes up, the performance gained by adaboost goes down.
-As shown in Fig~\ref{fig:dn_ad_val_acc}, when DTC's depth equals to 3, as the number of weak learner goes up, Adaboost has better performance.
-When DTC's depth equals to 5, Adaboost's performance is the worst.
-\par
-Now, we cann draw the following conclusions: \\
-1. Weaker learner gets larger performance gain in Adaboost. \\
-2. Very Strong weak learner tends to have overfitting problem in Adaboost. \\
-3. More weak learner boost the performance in Adaboost when weak learner is not very strong. \par
-
 \begin{figure}[!hbt]
@@
 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{n_ad_acc}
+		\includegraphics[width=\columnwidth]{reg_val_mae}
 		% Create a subtitle for the figure.
-		\caption{Adaboost accuracy with different number of DTC ($depth=1$).}
+		\caption{MF $MAE_{val}$ under different regularizer settings.}
 		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:n_ad_acc}
+		\label{fig:reg_val_mae}
 	\end{center}
@@
 
-\begin{figure}[!hbt]
-	% Center the figure.
+\subsection{Final Performance}
+In this section, we report the final performance under best settings, e.g. $h = 10$, $loss_{fn} = HB$ and $regularizer = L2$. Best result can be found in Table~\ref{tab:final_performance}. \par
+\begin{table}[!hbt]
+	% Center the table
 	\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{dn_ad_tr_acc}
-		% Create a subtitle for the figure.
-		\caption{Adaboost accuracy with different number of DTC ($depth = 1, 2, 3, 4, 5$) in training set.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:dn_ad_tr_acc}
+		% Title of the table
+		\caption{MF's best performance under best settings.}
+		\label{tab:final_performance}
+		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
+		\begin{tabular}{|c|c|c|}
+			\hline
+			$MAE_{train}$  & $MAE_{val}$ & $MAE_{test}$ \\
+			\hline
+		      0.6342 & 0.7246 & 0.7294\\
+			\hline
+		\end{tabular}
 	\end{center}
-\end{figure} \par
-
-\begin{figure}[!hbt]
-	% Center the figure.
-	\begin{center}
-		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
-		\includegraphics[width=\columnwidth]{dn_ad_val_acc}
-		% Create a subtitle for the figure.
-		\caption{Adaboost accuracy with different number of DTC ($depth = 1, 2, 3, 4, 5$) in validation set.}
-		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
-		\label{fig:dn_ad_val_acc}
-	\end{center}
-\end{figure} \par
+\end{table} \par
 
 \section{Conclusion}
-In this report, we explore Adaboost algorithm.
-Specifically, we explore the weak learner's performance and number of weak learner in Adaboost.
-We draw the conclusions that weaker learner can get more performance gain in Adaboost and stronger learner tends to have overfitting problem in Adaboost.
-And finally we report the performance on test set under the best validation setting.
+In this report, we explore Matrix Factorization algorithm.
+Specifically, we explore the hidden dimension $h$, loss function and regularizer in MF.
+We oberseve that smaller $h$ causes under-fitting problem while bigger $h$ causes over-fitting problem.
+Under the settings that using Huber Loss as loss function and L2 as regularizer, the best perfomance can be obtained.
 \par

### 2019-11-18 setup.py

@@ -2,7 +2,7 @@ from setuptools import setup, find_packages
 
 setup(
     name='simple_machine_learning',
-    version='0.1.4',
+    version='0.1.5',
     description='simple: simple machine learning framework.',
     classifiers=[
         'License :: OSI Approved :: MIT License',

### 2019-11-18 simple_ml/example/exp5/exp5.py

@@ -1,17 +1,11 @@
 import numpy as np
 
-from sklearn.datasets import load_svmlight_file
-from sklearn.model_selection import train_test_split
-
-from simple_ml.utils.distance import euclidean
-from simple_ml.preprocessing.general import Standardizer
-from simple_ml.linear.model import LinearRegression, RidgeRegression
 from simple_ml.nn.layer import Factorization, Input
 from simple_ml.nn.model import Model
-from simple_ml.nn.initializer import zeros, ones
-from simple_ml.nn.regularizer import L2_Regularizer, L1_Regularizer
+from simple_ml.nn.regularizer import L2_Regularizer, L1_Regularizer, L1L2_Regularizer
+from simple_ml.nn.loss import MAE, MSE, HuberLoss
 from simple_ml.nn.optimizer import SGD, Momentum, Adam, RMSProp
-from simple_ml.utils.metric import accuracy, absolute_error, square_error
+from simple_ml.utils.metric import absolute_error
 
 import matplotlib.pyplot as plt
 
@@ -65,7 +59,7 @@ def dlr():
     # out = Factorization(a_dim=num_user, b_dim=num_item, k=10)(Inputs)
     model = Model(Inputs, out)
     # model.compile('MSE', optimizer=Adam(lr=0.001))
-    model.compile('HB', optimizer=Adam(lr=0.001))
+    model.compile(HuberLoss(), optimizer=Adam(lr=0.001))
     model.fit(X_train, y_train,
               verbose=10, epochs=300,
               validation_data=(X_val, y_val),
